---
title: "outside halibut"
author: "Philina English"
date: "18/05/2021"
output: html_document
---

```{r}
# setwd(here::here()) # for RStudio Jobs
library(dplyr)
library(ggplot2)
library(sdmTMB)
# devtools::install_github("seananderson/ggsidekick")
library(ggsidekick) # for fourth_root_power_trans
theme_set(ggsidekick::theme_sleek())

# data <- gfdata::get_ll_hook_data("Yelloweye Rockfish", ssid = c(36))
# 
# d1 <- gfdata::get_survey_sets("Yelloweye Rockfish", ssid = c(36))

```

```{r}
convert2utm <- function(df, coords = c("X", "Y"), out_crs = 3156) {
  x <- sf::st_as_sf(df,
    coords = coords, crs = 4326
  ) %>%
    sf::st_transform(crs = out_crs) %>%
    sf::st_coordinates() %>%
    as.data.frame()
  x$X <- x$X / 100000
  x$Y <- x$Y / 100000
  dplyr::bind_cols(x,
    df[, which(!names(df) %in% coords), drop = FALSE])
}

expand_prediction_grid <- function(grid, years) {
  nd <- do.call("rbind",
    replicate(length(years), grid, simplify = FALSE))
  nd[["year"]] <- rep(years, each = nrow(grid))
  nd
}
```

Model diagnostics function
```{r}
get_diag <- function(m, response = "catch_count", variable = "depth_scaled", colour_var = "depth_m", start_year = 2007) {
  predictions <- predict(m)
  predictions$residuals <- residuals(m)
  
  predictions <- predictions %>% filter (year >= start_year)
  predictions$est_exp <- exp(predictions$est)

  print("R^2:")
  r2 <- cor(predictions$est, predictions[[response]])^2
  print(r2)

  print("")
  print("AIC:")
  print(AIC(m))

  print("")
  print("MSE:")
  print(mean(predictions$residuals^2))
  
  plot_map <- function(dat, column = "est") {
    ggplot(dat, aes_string("X", "Y", colour = column)) +
      geom_point(alpha = 0.5) +
      coord_fixed()+
      gfplot::theme_pbs() 
  }

  g <- plot_map(predictions, "est") +
    scale_colour_viridis_c() +
    ggtitle("Prediction (fixed effects + all random effects)")
  print(g)

  # g <- plot_map(predictions, "est_non_rf") +
  #   ggtitle("Prediction (fixed effects only)") +
  #   scale_colour_viridis_c()
  # print(g)
# 
#   g <- plot_map(predictions, "est_rf") +
#     ggtitle("All random effects only") +
#     scale_colour_gradient2()
#   print(g)

  g <- plot_map(predictions, "omega_s") +
    ggtitle("Spatial random effects only") +
    scale_colour_gradient2()
  print(g)

  g <- plot_map(predictions, "epsilon_st") +
    ggtitle("Spatiotemporal random effects only") +
    facet_wrap(~year) +
    scale_colour_gradient2()
  print(g)

  g <- plot_map(predictions, "residuals") +
    ggtitle("Residuals") +
    facet_wrap(~year) +
    scale_colour_gradient2()
  print(g)
  
  g <- ggplot(predictions, aes_string("est_exp", response)) +
    geom_point(alpha = 0.2) +
    facet_wrap(~year) +
    coord_fixed() +
    geom_abline()+
    gfplot::theme_pbs() 
  print(g)

  g <- ggplot(predictions, aes(est, residuals)) +
    geom_point(alpha = 0.2) +
    geom_smooth()+
    gfplot::theme_pbs() 
  print(g)
  
  g <- ggplot(predictions, aes_string(variable, "residuals", colour = colour_var)) +
    geom_point(alpha = 0.4, size = 1.2) +
    geom_smooth(colour="grey", size = 1.2) +
    scale_colour_viridis_c(option = "B", direction = -1, begin = 0, end = 0.7, 
      limits= c(min(predictions[colour_var]), max(predictions[colour_var]))) + #, trans= sqrt
    # facet_wrap(~year, scales = "free_x")+
    gfplot::theme_pbs() + theme(
      axis.text.y = element_text(size = 14),
      axis.text.x = element_blank(), axis.ticks.x = element_blank())
  print(g)
  
  g <- ggplot(predictions, aes_string(variable, "residuals", colour = colour_var)) +
    geom_point(alpha = 0.4, size = 0.7) +
    geom_smooth(colour="grey", size = 0.7) +
    scale_colour_viridis_c(option = "B", direction = -1, begin = 0, end = 0.7, 
      limits= c(min(predictions[colour_var]), max(predictions[colour_var]))) + #, trans= sqrt
    facet_wrap(~year, scales = "free_x")+
    gfplot::theme_pbs() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
  print(g)

}
```

# combine event and hook data if not done already
```{r}
hook_adjusted_data <- "data-generated/halibut_hook_adjusted_36.rds"
if (!file.exists(hook_adjusted_data)) {
data <- readRDS("data/halibut-hook-dat36.rds")
d1 <- readRDS("data/halibut-surv-sets.rds") %>% filter(survey_abbrev=="HBLL OUT S")

# the following code should deal with the issue of 0 baited hooks being observed.
adjust <- data %>%
  group_by(year, fishing_event_id) %>%
  mutate(total_hooks = count_target_species + count_non_target_species +
    count_bait_only + count_empty_hooks - count_bent_broken) %>%
  mutate(count_bait_only = replace(count_bait_only, which(count_bait_only == 0), 1)) %>%
  mutate(prop_bait_hooks = count_bait_only / total_hooks) %>%
  mutate(hook_adjust_factor = -log(prop_bait_hooks) / (1 - prop_bait_hooks)) %>%
  mutate(expected_catch = round(count_target_species * hook_adjust_factor))

# find out which events are in hook data but not set data:
setdiff(data$fishing_event_id, d1$fishing_event_id)

hook_adjusted_data <- left_join(d1, adjust, by = c("fishing_event_id", "year"))

saveRDS(hook_adjusted_data, file = "data-generated/halibut_hook_adjusted_36.rds")
}
```

# add block ids and offsets
```{r}
f <- "data-generated/halibut-surv-36-blocks.rds"
if (file.exists(f)) {
  d <- readRDS(f)
} else {
d <- readRDS("data/halibut-surv-sets.rds") %>% filter(survey_abbrev=="HBLL OUT S")
  block_ids <- readRDS("data/survey-blocks-36.rds") 
  d <- dplyr::left_join(d, block_ids)
  d$block_designation <- as.numeric(d$block_designation)
  saveRDS(d, file = "data-generated/halibut-surv-36-blocks.rds")
}

hook <- readRDS("data-generated/halibut_hook_adjusted_36.rds") %>%
  select(
    survey_series_id, year, fishing_event_id, total_hooks, prop_bait_hooks,
    hook_adjust_factor, expected_catch
  )

d <- left_join(d, hook, by = c("survey_series_id", "year", "fishing_event_id"))

d <- d %>%
  select(
    survey_abbrev, year, longitude, latitude, catch_count, hook_count,
    grouping_code, depth_m, block_designation, hook_adjust_factor, prop_bait_hooks
  ) %>% mutate(lon = longitude, lat = latitude) %>%
  rename(survey = survey_abbrev, block = block_designation)

d_utm <- convert2utm(d, coords = c("lon", "lat"))
d_utm <- filter(d_utm, grouping_code > 270 & grouping_code < 330) # not all part of survey

load("data/hbll_s_grid.rda")

d_utm$depth_log <- log(d_utm$depth_m)
d_utm$depth_centred <- d_utm$depth_log - mean(d_utm$depth_log)
d_utm$depth_mean <- mean(d_utm$depth_log)
d_utm$depth_sd <- sd(d_utm$depth_centred)
d_utm$depth_scaled <- d_utm$depth_centred / sd(d_utm$depth_centred)
d_utm$Y_cent <- d_utm$Y - mean(d_utm$Y)
d_utm$X_cent <- d_utm$X - mean(d_utm$X)
d_utm$area_swept <- d_utm$hook_count * 0.0024384 * 0.009144 * 1000
d_utm$offset_area_swept <- log(d_utm$area_swept)
d_utm$offset_area_hook <- log(d_utm$area_swept / d_utm$hook_adjust_factor)

s_grid_utm <- convert2utm(hbll_s_grid$grid, coords = c("X", "Y"))

s_grid_utm$longitude <- hbll_s_grid$grid$X 
s_grid_utm$latitude <- hbll_s_grid$grid$Y 

s_grid_utm$offset_area_hook <- mean(d_utm$offset_area_hook)
s_grid_utm$offset_area_swept <- mean(d_utm$offset_area_swept)
s_grid_utm$hook_adjust_factor <- mean(d_utm$hook_adjust_factor)
s_grid_utm$hook_count <- 100 #mean(d_utm$hook_count)
s_grid_utm$offset <- log(100)

years <- sort(unique(d_utm$year))
s_grid_utm <- expand_prediction_grid(s_grid_utm, years = years) %>%
  mutate(depth_centred = log(depth) - mean(d_utm$depth_log)) %>%
  mutate(depth_scaled = depth_centred / sd(d_utm$depth_centred))
s_grid_utm <- mutate(s_grid_utm, Y_cent = Y - mean(d_utm$Y))
s_grid_utm <- mutate(s_grid_utm, X_cent = X - mean(d_utm$X))
```


```{r }

sp <- make_mesh(d_utm, c("X", "Y"), n_knots = 200)
plot(sp)
# png("figs/hbll-outside-S-spde.png", width = 7, height = 7, units = "in", res = 180)
```

```{r}
glimpse(d_utm)
```

# just depth
```{r}
# m0 <- sdmTMB(
#       formula = catch_count ~ 0 + as.factor(year) +
#           depth_scaled + I(depth_scaled^2),
#       data = d_utm,
#       spde = sp,
#       time = "year",
#       silent = FALSE,
#       anisotropy = TRUE,
#       #cores = cores,
#       reml = TRUE,
#       family = nbinom2(link = "log")
#     )
# saveRDS(m0, file = "models/halibut-m0-depth-200kn.rds")
m0  <-  readRDS(file = "models/halibut-m0-depth-200kn.rds")
m0
get_diag(m0)
```

```{r}
d_utm$offset <- d_utm$offset_area_hook

m1 <- sdmTMB(
      formula = catch_count ~ 0 + as.factor(year) + depth_scaled + I(depth_scaled^2) + offset,
      data = d_utm,
      spde = sp,
      time = "year",
      silent = FALSE,
      anisotropy = TRUE,
      #cores = cores,
      reml = TRUE,
      family = nbinom2(link = "log")
    )
saveRDS(m1, file = "models/halibut-m1-offset-area-hook-200kn.rds")

# m1  <- readRDS(file = "models/halibut-m1-offset-area-hook-200kn.rds")
m1
get_diag(m1)
```

# estimate effect of hook area 
```{r}
m1b <- sdmTMB(
      formula = catch_count ~ 0 + as.factor(year) + depth_scaled + I(depth_scaled^2) + offset_area_hook,
      data = d_utm,
      spde = sp,
      time = "year",
      silent = FALSE,
      anisotropy = TRUE,
      #cores = cores,
      reml = TRUE,
      family = nbinom2(link = "log")
    )
saveRDS(m1b, file = "models/halibut-m1b-area-hook-200kn.rds")
# m1b  <- readRDS(file = "models/halibut-m1b-area-hook-200kn.rds")
m1b
get_diag(m1b)
```

# area swept worse than area hook
```{r}
# d_utm$offset <- d_utm$offset_area_swept
# 
# m2 <- sdmTMB(
#       formula = catch_count ~ 0 + as.factor(year) +
#           depth_scaled + I(depth_scaled^2) + offset,
#       data = d_utm,
#       spde = sp,
#       time = "year",
#       silent = FALSE,
#       anisotropy = TRUE,
#       #cores = cores,
#       reml = TRUE,
#       family = nbinom2(link = "log")
#     )
# saveRDS(m2, file = "models/halibut-m2-offset-area-swept-200kn.rds")
m2  <-  readRDS(file = "models/halibut-m2-offset-area-swept-200kn.rds")
m2
get_diag(m2)
```

# estimate effect of area swept better AIC but worse MSE than area hook 
```{r}
m2b <- sdmTMB(
      formula = catch_count ~ 0 + as.factor(year) +
          depth_scaled + I(depth_scaled^2) + offset_area_swept,
      data = d_utm,
      spde = sp,
      time = "year",
      silent = FALSE,
      anisotropy = TRUE,
      #cores = cores,
      reml = TRUE,
      family = nbinom2(link = "log")
    )
saveRDS(m2b, file = "models/halibut-m2b-area-swept-200kn.rds")

# m2b  <-  readRDS(file = "models/halibut-m2b-area-swept-200kn.rds")
m2b
get_diag(m2b)
```
# just an estimate for the hook adjustment factor
## second best AIC to model predicting effect of area swept
```{r}
# m3 <- sdmTMB(
#       formula = catch_count ~ 0 + as.factor(year) +
#           depth_scaled + I(depth_scaled^2) +
#           hook_adjust_factor,
#       data = d_utm,
#       spde = sp,
#       time = "year",
#       silent = FALSE,
#       anisotropy = TRUE,
#       #cores = cores,
#       reml = TRUE,
#       family = nbinom2(link = "log")
#     )
# saveRDS(m3, file = "models/halibut-m3-hook-factor-200kn.rds")

m3  <- readRDS(file = "models/halibut-m3-hook-factor-200kn.rds")
m3
get_diag(m3)
```

# use swept area offset and estimate hook adjustment
```{r}
d_utm$offset <- d_utm$offset_area_swept

m4 <- sdmTMB(
      formula = catch_count ~ 0 + as.factor(year)+
          depth_scaled + I(depth_scaled^2) +
          hook_adjust_factor +
          offset,
      data = d_utm,
      spde = sp,
      time = "year",
      silent = FALSE,
      anisotropy = TRUE,
      #cores = cores,
      reml = TRUE,
      family = nbinom2(link = "log")
    )
saveRDS(m4, file = "models/halibut-m4-hookfact-offset-area-swept-200kn.rds")
# m4  <-  readRDS(file = "models/halibut-m4-hookfact-offset-area-swept-200kn.rds")
m4
get_diag(m4)
```

# estimate swept area and hook adjustment
```{r}
# m4b <- sdmTMB(
#       formula = catch_count ~ 0 + as.factor(year)+
#           depth_scaled + I(depth_scaled^2) +
#           hook_adjust_factor +
#           offset_area_swept,
#       data = d_utm,
#       spde = sp,
#       time = "year",
#       silent = FALSE,
#       anisotropy = TRUE,
#       #cores = cores,
#       reml = TRUE,
#       family = nbinom2(link = "log")
#     )
# saveRDS(m4b, file = "models/halibut-m4b-hookfact-area-swept-200kn.rds")
m4b  <-  readRDS(file = "models/halibut-m4b-hookfact-area-swept-200kn.rds")
m4b
get_diag(m4b)
```


# Try with more knots
```{r }
sp4 <- make_mesh(d_utm, c("X", "Y"), n_knots = 400)
plot(sp4)
# png("figs/hbll-outside-S-spde.png", width = 7, height = 7, units = "in", res = 180)
```


# estimate swept area and hook adjustment
```{r}
m4c <- sdmTMB(
      formula = catch_count ~ 0 + as.factor(year)+
          depth_scaled + I(depth_scaled^2) +
          hook_adjust_factor +
          offset_area_swept,
      data = d_utm,
      spde = sp4,
      time = "year",
      silent = FALSE,
      anisotropy = TRUE,
      #cores = cores,
      reml = TRUE,
      family = nbinom2(link = "log")
    )
saveRDS(m4c, file = "models/halibut-m4c-hookfact-area-swept-400kn.rds")
# m4c  <-  readRDS(file = "models/halibut-m4c-hookfact-area-swept-400kn.rds")
m4c
get_diag(m4c)
```


# offset of hook_count
```{r}
d_utm$offset <- log(d_utm$hook_count)

m5 <- sdmTMB(
      formula = catch_count ~ 0 + as.factor(year) + # hook_adjust_factor + # currently leaving out
          depth_scaled + I(depth_scaled^2) +
          offset,
      data = d_utm,
      spde = sp4,
      ar1_fields = T,
      time = "year",
      silent = FALSE,
      anisotropy = TRUE,
      #cores = cores,
      reml = TRUE,
      family = nbinom2(link = "log")
    )
saveRDS(m5, file = "models/halibut-m5-hook-count-400kn-AR1.rds")
# m5  <-  readRDS(file = "models/halibut-m5-hook-count-400kn-AR1.rds")
m5
tidy(m5, "ran_pars",conf.int = TRUE)
get_diag(m5)
```

# spatial only model
```{r}
# d_utm$offset <- log(d_utm$hook_count)
# 
# m5s <- sdmTMB(
#       formula = catch_count ~ 0 + as.factor(year) + # hook_adjust_factor + # currently leaving out
#           depth_scaled + I(depth_scaled^2) +
#           offset,
#       data = d_utm,
#       spde = sp4,
#       # ar1_fields = T,
#       # time = "year",
#       silent = FALSE,
#       anisotropy = TRUE,
#       #cores = cores,
#       reml = TRUE,
#       family = nbinom2(link = "log")
#     )
# saveRDS(m5s, file = "models/halibut-m5-hook-count-400kn-spatial.rds")
m5s  <-  readRDS(file = "models/halibut-m5-hook-count-400kn-spatial.rds")
m5s
tidy(m5s, "ran_pars",conf.int = TRUE)
get_diag(m5s)
```

# Predictions from best model
```{r}
# p <- predict(m5, newdata = s_grid_utm, se_fit = F, re_form = NULL, return_tmb_object = T)
# saveRDS(p, "models/halibut-m5-AR1-predictions.rds")
```

```{r}
plot_map <- function(dat, column, wrap = TRUE) {
  gg <- ggplot(data = dat) +
    geom_tile(mapping = aes(X, Y, fill = {{ column }}), width = 0.025, height = 0.025) +
    coord_fixed() +
    scale_fill_viridis_c(option = "D")
  if (wrap) gg + facet_wrap(~year) else gg
}

# p <- readRDS("models/halibut-m4c-AR1-predictions.rds")
p <- readRDS("models/halibut-m5-AR1-predictions.rds")
g <- plot_map(p$data, exp(est)) +
  scale_fill_viridis_c(trans = ggsidekick::fourth_root_power_trans(), option = "D") +
  labs(
    fill = "Estimated\nadjusted\ncount",
    size = "Observed\nadjusted\ncount"
  ) +
  geom_point(
    data = d_utm, pch = 21, mapping = aes(
      x = X, y = Y,
      size = (catch_count / hook_count)*100
    ),
    inherit.aes = FALSE, colour = "grey20", alpha = 0.5
  ) +
  scale_size_area(max_size = 7)
g
```



```{r}

  gg <- ggplot(filter(p$data, year == 2020)) +
    geom_tile(mapping = aes(longitude, latitude, fill = exp(est)), width = 0.06, height = 0.025) +
    coord_fixed() +
  scale_fill_viridis_c(trans = ggsidekick::fourth_root_power_trans(), option = "D") +
  labs(
    fill = "Estimated\nadjusted\ncount",
    size = "Observed\nadjusted\ncount"
  ) +
  geom_point(
    data = filter(d_utm, year == 2020), pch = 21, mapping = aes(
      longitude, latitude,
      size = (catch_count / hook_count)*100
    ),
    inherit.aes = FALSE, colour = "grey20", alpha = 0.5
  ) +
  scale_size_area(max_size = 7)
gg
```

# Add court defined area shape file

```{r}
library(sf)
# library(raster)
focal_area <-sf::st_read(dsn="shape-files/taaqwiihak_areaVer2.shp",layer="taaqwiihak_areaVer2")
focal_area <- sf::st_transform(focal_area, crs = 4326)

# make prediction grid st 

s_grid_3cd <- filter(s_grid_utm, latitude<50.5) 

s_grid_3cd_sf <- st_as_sf(s_grid_3cd, coords = c("longitude", "latitude"))
st_crs(s_grid_3cd_sf) <- 4326 # set the coordinate reference system
s_grid_3cd_sf

intersected <- sf::st_intersects(s_grid_3cd_sf, focal_area)

# cda <- which(lengths(intersected) > 0)
cda_grid_sf <- s_grid_3cd_sf[which(lengths(intersected) > 0), ]
noncda_grid_sf <- s_grid_3cd_sf[which(lengths(intersected) == 0), ]

sfc_as_cols <- function(x, names = c("x","y")) {
  stopifnot(inherits(x,"sf") && inherits(sf::st_geometry(x),"sfc_POINT"))
  ret <- sf::st_coordinates(x)
  ret <- tibble::as_tibble(ret)
  stopifnot(length(names) == ncol(ret))
  x <- x[ , !names(x) %in% names]
  ret <- setNames(ret,names)
  dplyr::bind_cols(x,ret)
}

cda_grid <- sfc_as_cols(cda_grid_sf, c("longitude", "latitude")) 
noncda_grid <- sfc_as_cols(noncda_grid_sf, c("longitude", "latitude")) 
st_geometry(cda_grid) <- NULL
st_geometry(noncda_grid) <- NULL
```

# Predictions for CDA only
```{r}
m5  <-  readRDS(file = "models/halibut-m5-hook-count-400kn-AR1.rds")
p_cda <- predict(m5, newdata = cda_grid, se_fit = F, re_form = NULL, return_tmb_object = T)
saveRDS(p_cda, "models/halibut-m5-AR1-predictions-cda.rds")

i_cda <- get_index(p_cda)
saveRDS(i_cda, "models/halibut-m5-AR1-index-cda.rds")

ggplot(i_cda, aes(year, est)) + geom_line() +
  geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.4) +
  xlab('Year') + ylab('Biomass estimate (metric tonnes)')

```


# Predictions outside CDA but within 3cd
```{r}
# m5  <-  readRDS(file = "models/halibut-m5-hook-count-400kn-AR1.rds")
p_3cd <- predict(m5, newdata = noncda_grid, se_fit = F, re_form = NULL, return_tmb_object = T)
saveRDS(p_3cd, "models/halibut-m5-AR1-predictions-3cd.rds")

i_3cd <- get_index(p_3cd)
saveRDS(i_3cd, "models/halibut-m5-AR1-index-3cd.rds")

ggplot(i_3cd, aes(year, est)) + geom_line() +
  geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.4) +
  xlab('Year') + ylab('Biomass estimate (metric tonnes)')

```


# or without time
```{r}
m5s  <-  readRDS(file = "models/halibut-m5-hook-count-400kn-spatial.rds")
sp_cda <- predict(m5s, newdata = cda_grid, se_fit = F, re_form = NULL, return_tmb_object = T)
saveRDS(ps, "models/halibut-m5-spatial-predictions-cda.rds")

i_cda_sp <- get_index(sp_cda)
# saveRDS(i_sp, "models/ye-m5-cda-spatial-index.rds")

sp_noncda <- predict(m5s, newdata = noncda_grid, se_fit = F, re_form = NULL, return_tmb_object = T)
saveRDS(ps, "models/halibut-m5-spatial-predictions-cda.rds")

i_noncda_sp <- get_index(sp_noncda)
# saveRDS(i_sp, "models/halibut-m5-cda-spatial-index.rds")

i_cda_sp$est / (i_cda_sp$est + i_noncda_sp$est)
```

# map all of S HBLL
```{r}
# creates coast lines for area defined in lat lon
load_coastll <- function(xlim_ll, ylim_ll, utm_zone, buffer = 0) {
  data("nepacLLhigh", package = "PBSmapping", envir = environment())
  np <- PBSmapping::clipPolys(nepacLLhigh,
    xlim = xlim_ll + c(-buffer, buffer),
    ylim = ylim_ll + c(-buffer, buffer)
  )
  # ll2utm(np, utm_zone = utm_zone)
}

coast <- load_coastll(
    range(d_utm$longitude) ,
    range(d_utm$latitude) ,
    utm_zone = 9
  )

load_boundaries <- function(utm_zone) {
  data("major", package = "PBSdata", envir = environment())
  gfplot:::ll2utm(major, utm_zone = utm_zone)
}

majorbound  <- load_boundaries(9)
# to see what's what
library(PBSmapping) # needs this for some reason
attributes(majorbound)$PolyData
bound3CDnorth <- fortify(majorbound) %>% 
  filter(PID %in% c(3,4)) %>%  filter(X > 400 & X < 600 & Y > 5550)%>% gfplot:::utm2ll(utm_zone = 9)

# predictions <- p$data %>% 
#   st_as_sf(crs = 4326, coords = c("longitude", "latitude")) 

# p_hal <- readRDS("models/halibut-m4c-AR1-predictions.rds")
p_hal <- readRDS("models/halibut-m5-AR1-predictions.rds")
gh <- ggplot(data = focal_area) +
  # plot predictions from best model with mean swept area and hook adjustment factor
  geom_tile(data = filter(p_hal$data, year == 2020), 
    aes(longitude, latitude, fill = exp(est)), width = 0.06, height = 0.025) +
  scale_fill_viridis_c(trans = ggsidekick::fourth_root_power_trans(), 
    option = "D", limits=c(0, 40), na.value = "yellow") +
  labs(
    fill = "Estimated\nadjusted\ncount",
    size = "Observed\nadjusted\ncount"
  ) +
  geom_point(
    data = filter(d_utm, year == 2020), #just most recent year
    # data = d_utm, # plot all years together
    pch = 21, mapping = aes(
      longitude, latitude,
      size = (catch_count / hook_count)*100
    ),
    inherit.aes = FALSE, colour = "grey10", alpha = 0.4
  ) +  scale_size_area(max_size = 4) + 
  geom_line(# add major management region boundaries
    data = bound3CDnorth,
    aes(X, Y), colour = "black", lty = 2, 
    inherit.aes = F
  ) +
  annotate("text", x = -129.5, y = 50.25, label = "3CD") +
  annotate("text", x = -129.5, y = 51.25, label = "5AB") +
  geom_sf(colour = "red", fill = NA) + # add focal area
  geom_polygon( # add coast outline
      data = coast, aes(x = X, y = Y, group = PID),
      fill = "grey87", col = "grey70", lwd = 0.2
    ) +
  xlab("")+ ylab("")+ # remove axis labels
  coord_sf(expand = F, ylim=c(48.5, 52.1))  +# trim points beyond grid boundaries
  ggtitle("HBLL observed and predicted Pacific Halibut catch per 100 hooks")
gh
ggsave("halibut-m5-AR1-2020-predictions.png", width = 6, height = 6)
```

```{r}
gh3cd <- ggplot(data = focal_area) +
   geom_tile(data = filter(p_cda$data, year == 2020),
   aes(longitude, latitude, fill = exp(est)), width = 0.06, height = 0.025) +
   geom_tile(data = filter(p_3cd$data, year == 2020),
    aes(longitude, latitude, fill = exp(est)), width = 0.05, height = 0.025) +
  scale_fill_viridis_c(
    trans = ggsidekick::fourth_root_power_trans(),
    limits=c(0, 7), na.value = "yellow",
    option = "D") +
  labs(
    fill = "Estimated\ncount\nin 3CD",
    size = "Observed\ncount"
  ) +
  geom_point(# plot all years together
    data = d_utm, pch = 21, mapping = aes(
      longitude, latitude,
      size = (catch_count / hook_count)*100
    ),
    inherit.aes = FALSE, colour = "grey10", alpha = 0.4
  ) +  scale_size_area(max_size = 4) + 
  geom_sf(colour = "red", fill = NA) + # add focal area
  geom_polygon( # add coast outline
      data = coast, aes(x = X, y = Y, group = PID),
      fill = "grey87", col = "grey70", lwd = 0.2
    ) +
  xlab("")+ ylab("")+ # remove axis labels
  coord_sf(expand = F, ylim=c(48.4, 50.6), xlim=c(-128.5, -125.15))  +# trim points beyond grid boundaries
  ggtitle("HBLL observed and predicted Pacific Halibut catch per 100 hooks")
gh3cd
ggsave("halibut-m5-AR1-2020-predictions-3cd.png", width = 6, height = 6)
```

```{r}
py <- readRDS("models/ye-m5-AR1-predictions.rds") 

pyd <- py$data %>% rename(ye_est = est) 
ph <- readRDS("models/halibut-m5-AR1-predictions.rds")
phd <- ph$data %>% rename(hal_est = est) %>% select(hal_est, X, Y, year)

ratio_df <- left_join(pyd, phd) %>% mutate(halibut = exp(hal_est), yelloweye = exp(ye_est), ye_per_hal = yelloweye/halibut)

gratio <- ggplot(data = focal_area) +
  # plot predictions from best model with mean swept area and hook adjustment factor
  geom_tile(data = filter(ratio_df, year == 2020), 
    aes(longitude, latitude, fill = ye_per_hal), width = 0.06, height = 0.025) +
  scale_fill_viridis_c(trans = ggsidekick::fourth_root_power_trans(), 
    # limits=c(0, 40), na.value = "yellow", 
    option = "D"
    ) +
  labs(
    fill = "Yelloweye\ncaught\nper halibut",
    size = "Observed\nhalibut\ncatch"
  ) +
  geom_point(# plot all years together
    data = d_utm, pch = 21, mapping = aes(
      longitude, latitude,
      size = (catch_count / hook_count)*100
    ),
    inherit.aes = FALSE, colour = "grey10", alpha = 0.4
  ) +  scale_size_area(max_size = 4) + 
  geom_line(# add major management region boundaries
    data = bound3CDnorth,
    aes(X, Y), colour = "black", lty = 2, 
    inherit.aes = F
  ) +
  annotate("text", x = -129.5, y = 50.25, label = "3CD") +
  annotate("text", x = -129.5, y = 51.25, label = "5AB") +
  geom_sf(colour = "red", fill = NA) + # add focal area
  geom_polygon( # add coast outline
      data = coast, aes(x = X, y = Y, group = PID),
      fill = "grey87", col = "grey70", lwd = 0.2
    ) +
  xlab("")+ ylab("")+ # remove axis labels
  coord_sf(expand = F, ylim=c(48.5, 52.1))  +# trim points beyond grid boundaries
  ggtitle("Estimated number of Yelloweye Rockfish caught per halibut")
gratio
ggsave("ye-per-halibut-w-hal-catch.png", width = 6, height = 6)

```
# try tv depth
### not useful
```{r}
# m5 <- sdmTMB(
#       formula = catch_count ~ 0 + as.factor(year)+
#           hook_adjust_factor +
#           offset_area_swept,
#       time_varying = ~ 0 + depth_scaled + I(depth_scaled^2),
#       data = d_utm,
#       spde = sp,
#       time = "year",
#       silent = FALSE,
#       anisotropy = TRUE,
#       #cores = cores,
#       reml = TRUE,
#       family = nbinom2(link = "log")
#     )
# saveRDS(m5, file = "models/halibut-m5-tv-depth-200kn.rds")
m5  <-  readRDS(file = "models/halibut-m5-tv-depth-200kn.rds")
m5
get_diag(m5)
```

```{r}
tvd <- gfranges::time_varying_density(m5, predictor = "depth")
tvd$x <- exp(tvd$x)
p <- gfranges::plot_mountains(tvd,
    variable_label = "Depth (m)",
    peaklines = F,
    mountains_only = F,
    xlimits = c(15, 270))
p
```


```{r}
# make_tv_depth_grid <- function(m){
#   expand.grid(
#     depth_scaled = seq(min(m$data$depth_scaled), max(m$data$depth_scaled), length.out = 100),
#     hook_adjust_factor = mean(m$data$hook_adjust_factor), 
#     offset_area_swept = mean(m$data$offset_area_swept), 
#     year = as.factor(unique(m$data$year))
#   )}
# 
# depth_grid <- make_tv_depth_grid(m5)
# 
# species_depth_profile <- function(m, depth_grid,
#   min_depth_m = 15, 
#   max_depth_m = 240,
#   min_year = min(m$data$year), 
#   response = "count"
#   ){
# 
#   p <- predict(m, newdata = depth_grid, se_fit = TRUE, re_form = NA)
#   p <- p %>% mutate(
#     Depth = exp(depth_scaled * m$data$depth_sd[1] + m$data$depth_mean[1]),
#     response = exp(est),
#     lowCI = exp(est - 1.96 * est_se),
#     highCI = exp(est + 1.96 * est_se))
#   
# g <- ggplot(filter(p, Depth > min_depth_m & year > min_year), 
#   aes(Depth, response,
#   ymin = lowCI, 
#   ymax = highCI, 
#   group = as.factor(year), fill = year, colour = year)) +
#   geom_ribbon(alpha = 0.1, colour = NA) +
#   geom_line(size = 0.5, alpha =0.85) +
#   scale_fill_viridis_c(option = "C") +
#   scale_colour_viridis_c(option = "C") +
#   coord_cartesian(xlim = c(min_depth_m, max_depth_m), ylim=c(0, quantile(p$Biomass, 1))) +
#   xlab("Depth (m)") +
#   gfplot::theme_pbs() 
# 
# if(response=="biomass") {
# g <- g + ylab("Biomass")
# }
# 
# if(response=="count") {
# g <- g + ylab("Individuals")
# }
# 
# g
# }
# 
# (tv_plot <- species_depth_profile(m5, depth_grid))
```

