---
title: "Annotated Bibliography"
author: |
  | Philina English
bibliography: pbs-rangeshifts.bib
csl: apa-cv.csl
output: html_document
#biblio-style: chicago-annote
---
# csl: smithsonian-institution-scholarly-press-note.csl
# csl: apa-cv
# csl: chicago-annotated-bibliography.csl
# csl: style-manual-australian-government-note.csl
# csl: chicago-note-bibliography-16th-edition.csl

# bookdown::pdf_document2:
#  toc: no

# bibliography: [packages.bib, papers.bib]
# biblio-style: apalike

```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
# I usually load my libraries up front to keep things organized
library(tidyverse)
library(bookdown)
library(knitr)
library(kableExtra)
library(ggthemes)
library(ggExtra)
library(stringr)
```


```{r}
# library(citr) # went to addin, insert citations, but too slow/didn't seem to work
```


```{r}
library(rbbt)
bbt_cite()
bbt_bib_zotero()
```

[@thorson_model-based_2016]


Key

(1) Citation

(2) Introduction 

(3) Aims & Research methods

(4) Scope

(5) Usefulness (to your research/ to a particular topic)

(6) Limitations

(7) Conclusions

(8) Reflection (explain how this work illuminates your topic or how it will fit in with your research)