---
title: "Biomass trend maps"
author: "Philina English"
date: '2019-06-07'
output: html_document
---

Choose one value for each parameter:

Species
```{r}
species <- "Quillback Rockfish"
species <- "Yelloweye Rockfish"
species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
species <- "Silvergray Rockfish"
species <- "Arrowtooth Flounder"
```

Region of interest
```{r}
region <- "Both odd year surveys"
region <- "West Coast Vancouver Island"
region <- "West Coast Haida Gwaii"
region <- "Queen Charlotte Sound"
region <- "Hecate Strait"
region <- "Both West Coast surveys"

## region <- "All synoptic surveys" # Probably not possible
```

Is a new spatial needed?
```{r}
update_spatial_model <- TRUE
update_spatial_model <- FALSE
```


Run all subsequent code...


```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(gfplot)
library(gfdata)
library(sdmTMB)
library(gfranges)
```



```{r}

if(region == "Both odd year surveys") {
survey <- c("SYN QCS","SYN HS")
model_ssid <- c(1,3)
years <- NULL
}

if(region == "West Coast Vancouver Island") {
survey <- c("SYN WCVI")
model_ssid <- c(4)
years <- NULL
}

if(region == "West Coast Haida Gwaii") {
survey <- c("SYN WCHG")
model_ssid <- c(16)
years <- NULL
}

if(region == "Queen Charlotte Sound") {
survey <- c("SYN QCS")
model_ssid <- c(1)
years <- NULL
}

if(region == "Hecate Strait") {
survey <- c("SYN HS")
model_ssid <- c(3)
years <- NULL
}

# if(region == "Both West Coast surveys") {
# survey <- c("SYN WCVI","SYN WCHG")
# model_ssid <- c(4,16)
# years <- NULL
# }

# if(region == "All synoptic surveys") {
# survey <- c("SYN QCS","SYN HS","SYN WCVI","SYN WCHG")
# model_ssid <- c(1,3,4,16)
# years <- NULL
# }

ssid_string <- paste0(model_ssid, collapse = "n")
spp <- gsub(" ", "-", gsub("\\/", "-", tolower(species)))
```

Make prediction grids for all surveys and years, if not done before.
```{r, message=FALSE, warning=FALSE}
try(nd_all <- readRDS("data/nd_all_synoptic.rds"))

if (!exists("nd_all")) {
bath <- readRDS("data/bathymetry-data")
# choose base year(s) to create grid from
dummy_year <- c(2005,2006)
dat <- bath$data %>% scale_survey_predictors()
# create grids for each ssid separately
ssid <- 1
survey_abbrev <- "SYN QCS"
nd_1 <- spatiotemporal_grid(dat, ssid, survey_abbrev, dummy_year)
unique(nd_1$year)

ssid <- 3
survey_abbrev <- "SYN HS"
nd_3 <- spatiotemporal_grid(dat, ssid, survey_abbrev, dummy_year)
unique(nd_3$year)

ssid <- 4
survey_abbrev <- "SYN WCVI"
nd_4 <- spatiotemporal_grid(dat, ssid, survey_abbrev, dummy_year)
unique(nd_4$year)

ssid <- 16
survey_abbrev <- "SYN WCHG"
nd_16 <- spatiotemporal_grid(dat, ssid, survey_abbrev, dummy_year)
unique(nd_16$year)

nd_all <- rbind(nd_1, nd_3, nd_4, nd_16) %>%
  mutate(year = as.numeric(year)) 
#nd <- nd %>% dplyr::mutate(shallow = ifelse(depth > 35, 0, 1))

saveRDS(nd_all, file = paste0("data/nd_all_synoptic.rds"))
}
```


Calculate maturity weighted biomass if not done before
```{r}
try(biomass <- readRDS(paste0("data/data-by-maturity-", spp,"-", ssid_string, ".rds")))

if (!exists("biomass")) {

survey_sets <- readRDS(paste0("raw/event-data-", spp, ""))
fish <- readRDS(paste0("raw/bio-data-", spp, ""))
bath <- readRDS("data/bathymetry-data")
# for POP, exclude sample with unusually large fish that are impossible given recorded catch weight
# fish <- fish[fish$fishing_event_id!=1506954,] 

maturity <- split_catch_maturity (survey_sets, fish, bath,
  #survey = c("SYN QCS","SYN HS","SYN WCVI","SYN WCHG"), 
  survey = survey,
  years = years,
  cutoff_quantile = c(.9995),
  plot = TRUE
)

saveRDS(maturity$data, file = paste0("data/data-by-maturity-", spp, "-", ssid_string, ".rds"))
}

```



```{r}
if(exists("maturity")) {
png(file = paste0("figs/", spp, "-mass-model-", ssid_string, ".png"),   # The directory you want to save the file in
res = 600,
units = 'in',
width = 8, # The width of the plot in inches
height = 10)
  
maturity$mass_model

dev.off()
print(maturity$mass_model)
}
```


```{r}
if(exists("maturity")) {
png(file = paste0("figs/", spp, "-maturity-", ssid_string, ".png"),   # The directory you want to save the file in
res = 600,
units = 'in',
width = 8, # The width of the plot in inches
height = 10)

maturity$maturity

dev.off()
print(maturity$maturity)
}
```

Run sdmTMB model (if not done previously).
```{r eval=FALSE}
if (update_spatial_model) {

biomass <- readRDS(paste0("data/data-by-maturity-", spp, "-", ssid_string, ".rds"))
data <- biomass %>% gfranges:::scale_survey_predictors()

nd <- nd_all %>% filter(ssid %in% model_ssid) 
data <- data %>% filter(ssid %in% model_ssid)

spde <- sdmTMB::make_spde(data$X, data$Y, n_knots = 500)
sdmTMB::plot_spde(spde)

if (any(names(data)=="adult_density")) {
  
adult_biomass <- sdmTMB::sdmTMB(data,
  adult_density ~ 0 + as.factor(year),
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  time = "year", spde = spde,
  family = tweedie(link = "log"),
  ar1_fields = TRUE, 
  include_spatial = TRUE,
  enable_priors = TRUE,
  # control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
  silent = FALSE
)

imm_biomass <- sdmTMB::sdmTMB(data,
  imm_density ~ 0 + as.factor(year),
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  time = "year", spde = spde,
  family = tweedie(link = "log"),
  ar1_fields = FALSE, 
  include_spatial = TRUE,
  enable_priors = TRUE,
  silent = FALSE
)

saveRDS(adult_biomass, file = paste0("data/model-mature-biomass-", spp, "-", ssid_string, ".rds"))

saveRDS(imm_biomass, file = paste0("data/model-imm-biomass-", spp, "-", ssid_string, ".rds"))

} else {

total_biomass <- sdmTMB::sdmTMB(dat,
  density ~ 0 + as.factor(year),
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  time = "year", spde = spde,
  family = tweedie(link = "log"),
  ar1_fields = TRUE, 
  include_spatial = TRUE,
  silent = FALSE
)

saveRDS(total_biomass, file = paste0("data/model-total-biomass-", spp, "-", ssid_string, ".rds"))

}
}
```


Calculate predicted values for available models, if needed
```{r, error=TRUE}
if (isFALSE(update_spatial_model)) {
  try(adult_predictions <- readRDS(paste0("data/predictions-", spp, "-", ssid_string, "-mature-biomass.rds")))
  try(imm_predictions <- readRDS(paste0("data/predictions-", spp, "-", ssid_string, "-imm-biomass.rds")))
  try(predictions <- readRDS(paste0("data/predictions-", spp, "-", ssid_string, "-total-biomass.rds")))
} 

if (!exists("adult_predictions")) {  
if (length(unique(fish$maturity_code))>2) {
    nd$year<- as.integer(nd$year)
      
    adult_biomass <- readRDS(paste0("data/model-mature-biomass-", spp, "-", ssid_string, ".rds"))
    adult_predictions <- predict(adult_biomass, newdata = nd)
    saveRDS(adult_predictions, file = paste0("data/predictions-", spp, "-", ssid_string, "-mature-biomass.rds"))
    
    imm_biomass <- readRDS(paste0("data/model-imm-biomass-", spp, "-", ssid_string, ".rds"))
    imm_predictions <- predict(imm_biomass, newdata = nd)
    saveRDS(imm_predictions, file = paste0("data/predictions-", spp, "-", ssid_string, "-imm-biomass.rds"))
    
  } else {
    rm(adult_predictions)
    rm(imm_predictions) 
    
    if (!exists(predictions)) {  
    total_biomass <- readRDS(paste0("data/model-total-biomass-", spp, "-", ssid_string, ".rds"))
    nd$year<- as.integer(nd$year)
    predictions <- predict(total_biomass, newdata = nd)
    saveRDS(predictions, file = paste0("data/predictions-", spp, "-", ssid_string, "-total-biomass.rds"))
    }
    }
}
  
if (exists("adult_predictions")) {
    adult_predictions$est_exp <- exp(adult_predictions$est)*10000
    imm_predictions$est_exp <- exp(imm_predictions$est)*10000
    
    adult_predictions$total_bio <- imm_predictions$est_exp + adult_predictions$est_exp
    imm_predictions$prop_imm <- imm_predictions$est_exp/(adult_predictions$est_exp+imm_predictions$est_exp)
    
    max_raster <- quantile(adult_predictions$est_exp, .9999)
    max_adult <-  round(max(adult_predictions$est_exp))

} else {  
    predictions$total_bio <- exp(predictions$est)*10000
    max_raster <- quantile(predictions$total_bio, .9999)
    max_bio <-  round(max(predictions$total_bio))
}
```

```{r, error=TRUE}
if (exists("adult_predictions")) {
p_adult <- plot_facet_map(adult_predictions, "est_exp", 
  transform_col = fourth_root_power, 
  raster_limits = c(0, max_raster),
  legend_position = "none"
  ) + 
  labs(fill="kg/ha") +
  ggtitle(paste0("", species, " mature biomass \n(max = ", max_adult, " kg/ha)"))
print(p_adult) 
} else { 
  p_adult <- plot_facet_map(predictions, "total_bio", 
    #raster_limits = c(0, max_raster),
    transform_col = fourth_root_power) + 
  labs(fill="kg/ha") +
  ggtitle(paste0("", species, " total biomass \n(max = ", max_bio, " kg/ha)"))
print(p_adult) 
  }
```



```{r, message=FALSE, warning=FALSE}
if (exists("adult_predictions")) {
  predictions <- adult_predictions 
} 

if ( 1 %in% model_ssid) {
out_mature1 <- make_vector_data(predictions,
  ssid = c(1),
  start_time = 2003,
  #start_time = 2005,
  skip_time = 2004,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 1, 2, 2, 2, 2),
  #indices = c(1, 1, 1, 2, 2, 2, 2),
  variable_names = "est_exp",
  thresholds = c(0.001) 
)
} else { out_mature1 <- NULL }

if ( 3 %in% model_ssid) {  
out_mature3 <- make_vector_data(predictions,
  ssid = c(3),
  start_time = 2005,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 2, 2, 2, 2),
  variable_names = "est_exp",
  thresholds = c(0.001) 
)
} else { out_mature3 <- NULL }


if ( 4 %in% model_ssid) {  
out_mature4 <- make_vector_data(predictions,
  ssid = c(4),
  start_time = 2004,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 1, 2, 2, 2, 2),
  variable_names = "est_exp",
  thresholds = c(0.001) 
)
} else { out_mature4 <- NULL }

  
if ( 16 %in% model_ssid) {  
out_mature16 <- make_vector_data(predictions,
  ssid = c(16),
  start_time = 2004,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 1, 2, 2, 2, 2),
  variable_names = "est_exp",
  thresholds = c(0.001) 
)
} else { out_mature16 <- NULL }
out_mature <- rbind(out_mature1, out_mature3, out_mature4, out_mature16)

if (length(unique(fish$maturity_code))<2) {
  out_total <- out_mature
} 
```


Optional plot of current total biomass 
```{r eval=FALSE}
if (exists("out_total")) {
current_biomass <- plot_vocc(out_total,
  fill_col = "var_1_e",
  fill_label = "Mean mature \nbiomass (kg/ha)\n in 2011-2017",
  raster_alpha = 1,
  viridis_option = "C",
  vec_aes = NULL,
  transform_col = fourth_root_power
)
current_biomass <- current_biomass +
  ggtitle(paste0("", species, " total biomass"))

current_biomass
}
```


```{r, error=TRUE}
if (exists("out_mature")) {
data <- out_mature
biotrend_ad <- plot_vocc(data,
  fill_col = "units_per_decade",
  fill_label = "Mature \nbiomass \ntrend \n(kg/ha/decade)",
  raster_alpha = 1,
  vec_aes = NULL,
  # axis_lables = TRUE,
  transform_col = fourth_root_power,
  legend_position = c(0.2, 0.25)
)+ ggtitle(paste0("", species, " ", min(unique(adult_predictions[["year"]])), "-", max(unique(adult_predictions[["year"]]))))
biotrend_ad
} else {
  biotrend_ad <- plot_vocc(out_total,
  fill_col = "units_per_decade",
  fill_label = "Biomass \ntrend \n(kg/ha/decade)",
  raster_alpha = 1,
  vec_aes = NULL,
  # axis_lables = TRUE,
  transform_col = fourth_root_power,
  legend_position = c(0.2, 0.25)
)+ ggtitle(paste0("", species, " ", min(unique(predictions[["year"]])), "-", max(unique(predictions[["year"]]))))
biotrend_ad
}
```


```{r}
if (exists("imm_predictions")) {
p_imm <- plot_facet_map(imm_predictions, "est_exp", transform_col = fourth_root_power, 
  raster_limits = c(0, max_raster)) + 
  labs(fill="kg/ha") +
  ggtitle(paste0("", species, " immature biomass \n "))
p_imm
} else {
  p_imm <- grid::grid.rect(gp=grid::gpar(col="white"))
}
```


```{r, message=FALSE, warning=FALSE}
if (exists("imm_predictions")) {
  predictions <- imm_predictions 

if ( 1 %in% model_ssid) {
out_im1 <- make_vector_data(predictions,
  ssid = c(1),
  start_time = 2003,
  #start_time = 2005,
  skip_time = 2004,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 1, 2, 2, 2, 2),
  #indices = c(1, 1, 1, 2, 2, 2, 2),
  variable_names = "est_exp",
  thresholds = c(0.001) 
)
} else { out_im1 <- NULL }

if ( 3 %in% model_ssid) {  
out_im3 <- make_vector_data(predictions,
  ssid = c(3),
  start_time = 2005,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 2, 2, 2, 2),
  variable_names = "est_exp",
  thresholds = c(0.001) 
)
} else { out_im3 <- NULL }


if ( 4 %in% model_ssid) {  
out_im4 <- make_vector_data(predictions,
  ssid = c(4),
  start_time = 2004,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 1, 2, 2, 2, 2),
  variable_names = "est_exp",
  thresholds = c(0.001) 
)
} else { out_im4 <- NULL }

  
if ( 16 %in% model_ssid) {  
out_im16 <- make_vector_data(predictions,
  ssid = c(16),
  start_time = 2004,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 1, 2, 2, 2, 2),
  variable_names = "est_exp",
  thresholds = c(0.001) 
)
} else { out_im16 <- NULL }
out_imm <- rbind(out_im1, out_im3, out_im4, out_im16)

} else { rm(out_imm) }

```

```{r}
if (exists("out_imm")) {
data <- out_im1
data <- out_imm
biotrend_im <- plot_vocc(data,
  fill_col = "units_per_decade",
  fill_label = "Immature \nbiomass \ntrend \n(kg/ha/decade)",
  raster_alpha = 1,
  vec_aes = NULL,
  transform_col = fourth_root_power,
  #axis_lables = TRUE,
  legend_position = c(0.2, 0.25)
) + ggtitle(paste0("", species, " ", min(unique(imm_predictions[["year"]])), "-", max(unique(imm_predictions[["year"]]))))
biotrend_im
} else { biotrend_im <- grid::grid.rect(gp=grid::gpar(col="white"))}
```


```{r}
if (exists("imm_predictions")) {

p_prop_imm <- plot_facet_map(imm_predictions, "prop_imm") + 
  labs(fill="% \nby mass") +
  ggtitle(paste0("", species, " proportion immature"))
print(p_prop_imm)

} else { p_prop_imm <- grid::grid.rect(gp=grid::gpar(col="white"))}
```

Retrieve (or calculate) predicted values for temperature
```{r, eval=FALSE}
# m_temp <- readRDS("../VOCC/data/m_temp_allyears.rds")
# temperature <- predict(m_temp, newdata = nd_all)
# saveRDS(temperature, file = "data/predicted_temp_allyears.rds")

temperature <- readRDS("data/predicted_temp_allyears.rds")
temperature <- filter(temperature, ssid %in% model_ssid)
```

```{r, eval=FALSE}
temp <-plot_facet_map(temperature, "est", transform_col = no_trans, viridis_option = "D") + 
  labs(fill="°C") +
  ggtitle("Bottom temperature")
print(temp)
```


```{r, eval=FALSE}
png(file = paste0("figs/exploratory-", spp, "-", ssid_string, ".png"),   # The directory you want to save the file in
res = 600,
units = 'in',
width = 9.5, # The width of the plot in inches
height = 12.5) # The height of the plot in inches

gridExtra::grid.arrange(
    p_adult, p_imm, 
    biotrend_ad, biotrend_im, 
    #current_biomass, 
    p_prop_imm, temp,
    nrow = 3)
dev.off()

```