---
title: "Spatiotemporal model of `r paste(params$species)` biomass"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Pacific Sand Lance"
    region: "Non-HG surveys"
    knots: 400
    # covs: "-sand-depth-roms"
    # covs: "-depth-roms"
    # covs: "-sand-depth-temp"
    # covs: "-mud-depth-temp"
    # covs: "-mud-sand-depth-temp"
    covs: "-sand-x-depth-temp" # doesn't converge
    REML: FALSE
    AR1: TRUE
    fixed_spatial: TRUE
    update_model: TRUE
    # update_model: FALSE
    update_model_check: TRUE
    update_predictions: TRUE
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 11, fig.height = 8.5,
  # fig.path=paste0("figs/", spp, "/"),
  echo = FALSE, warning = FALSE, message = FALSE
)
library(dplyr)
library(ggplot2)
library(gfplot)
library(gfdata)
library(sdmTMB)
library(gfranges)

theme_set(
    gfplot::theme_pbs(base_size = 14) 
)
```

```{r formula}
if(params$covs == "-sand-depth-roms"){
mod.formula <- as.formula(paste0(
  "density ~ 0 + as.factor(year_pair) + 
  s(sandy_scaled, k = 3) + 
  s(depth_scaled, k = 3) + 
  s(roms_scaled, k = 3)"
  ))
clim_cov <- "roms"
}

if(params$covs == "-depth-roms"){
mod.formula <- as.formula(paste0(
  "density ~ 0 + as.factor(year_pair) + 
  s(depth_scaled, k = 3) + 
  s(roms_scaled, k = 3)"
  ))
clim_cov <- "roms"
}

if(params$covs == "-depth-temp"){
mod.formula <- as.formula(paste0(
  "density ~ 0 + as.factor(year_pair) + 
  s(depth_scaled, k = 3) + 
  s(temp_scaled, k = 3)"
  ))
clim_cov <- "temp"
}

if(params$covs == "-sand-depth-temp"){
mod.formula <- as.formula(paste0(
  "density ~ 0 + as.factor(year_pair) + 
  s(sandy_scaled, k = 3) + 
  s(sandy_scaled, by = shallow, k = 3) + 
  s(depth_scaled, k = 3) + 
  s(temp_scaled, k = 3)"
  ))
clim_cov <- "temp"
}

if(params$covs == "-mud-depth-temp"){
mod.formula <- as.formula(paste0(
  "density ~ 0 + as.factor(year_pair) + 
  s(muddy_scaled, k = 2) + 
  s(depth_scaled, k = 3) + 
  s(temp_scaled, k = 3)"
  ))
clim_cov <- "temp"
}

if(params$covs == "-mud-sand-depth-temp"){
mod.formula <- as.formula(paste0(
  "density ~ 0 + as.factor(year_pair) + 
  muddy_scaled + 
  sandy_scaled + 
  s(depth_scaled, k = 3) + 
  s(temp_scaled, k = 3)"
  ))
clim_cov <- "temp"
}

if(params$covs == "-sand-x-depth-temp"){
mod.formula <- as.formula(paste0(
  "density ~ 0 + as.factor(year_pair) + 
  sandy_scaled + 
  s(depth_scaled, k = 3) + 
  te(depth_scaled, sandy_scaled, k = 3, m=1) + 
  s(temp_scaled, k = 3)"
  ))
clim_cov <- "temp"
}
```


```{r params}
species <- params$species
region <- params$region
covs <- params$covs
knots <- params$knots
# REML <- params$REML
# AR1 <- params$AR1

paste("region =", params$region)
paste("climate covariate =", clim_cov)
paste("model label =", params$covs)
paste("knots =", params$knots)
paste("REML =", params$REML)
paste("AR1 =", params$AR1)
paste("fixed spatial =", params$fixed_spatial)
paste("formula =", mod.formula[3])
```

```{r, message=FALSE, warning=FALSE}
spp <- gsub(" ", "-", gsub("\\/", "-", tolower(species)))

# folder to hold figs for this species
dir.create(file.path("figs", spp))
dir.create(file.path("data", spp))

if (region == "Both odd year surveys") {
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")
  years <- NULL
}

if (region == "West Coast Vancouver Island") {
  survey <- c("SYN WCVI")
  model_ssid <- c(4)
  ssid_string <- paste0(model_ssid, collapse = "n")
  years <- NULL
}

if (region == "Non-HG surveys") {
  survey <- c("SYN QCS", "SYN HS", "SYN WCVI")
  model_ssid <- c(1, 3, 4)
  ssid_string <- paste0(model_ssid, collapse = "n")
  years <- NULL
}
```

# Build spatiotemporal density model
Load and filter data 
```{r}
# # if on dfo network trawl data can be retrieved
# events <- gfdata::get_survey_sets(species, ssid = c(1, 3, 4, 16))
# saveRDS(events, file = paste0("data/event-data-", spp, "")) 
# biomass <- readRDS(paste0("data/event-data-", spp, ""))

# on PE's system
biomass <- readRDS(paste0("../VOCC/raw/event-data-", spp, ""))

# trace samples aren't always recorded in 'density_kgpm2' variable
# but are recorded in 'catch_count'
# likewise larger catches are recorded as 0 in 'catch_count'
biomass <- biomass %>% mutate(
  present = if_else(density_kgpm2 > 0, 1, if_else(catch_count > 0, 1, 0)),
  density = (if_else(density_kgpm2 > 0, density_kgpm2, 
    # use roughly the min recorded density for these trace samples
    if_else(catch_count > 0, 1e-07, 0))) * 10000  # convert kgpm2 to kg per ha
  ) %>% select(fishing_event_id, year, present, density) %>% 
  # don't currently have covariate layers for 2019
  filter(year < 2019)

# get substrate data
covars <- readRDS("data/event-covariates.rds") %>% select(-geometry)
data <- dplyr::left_join(biomass, covars) 

# get ctd sensor data
sensor <- readRDS("~/github/dfo/gfranges/analysis/tmb-sensor-explore/data/all-sensor-data-processed.rds") %>% select(-X, -Y, -lat, -lon)
data <- left_join(data, sensor) %>% 
  # remove depth data to bring in complete set later
  select(-exclude, -akima_depth, -depth_edit, -log_depth, -depth_bath)

# get ROMS mean temperature for April through September each year
roms <- readRDS("~/github/dfo/gfranges/analysis/tmb-sensor-explore/data/roms_temp_by_events2.rds") %>% select(fishing_event_id, roms)
data <- left_join(data, roms) 

# get interpolated bathymetry data for comparison with sensor recorded depths
bath <- readRDS("data/bathymetry-data")
bath <- bath$data %>% select(X,Y, ssid, fishing_event_id, depth_bath = depth)  

d <- left_join(data, bath) %>% mutate(
  depth_sam = depth,# rename sensor depth
  depth = coalesce(depth, depth_bath),# use bath depth if sensor depth missing
  raw_depth = depth, # create 'depth' var that's actually log depth for scaling
  log_depth = log(depth), depth = log(raw_depth),
  shallow = if_else(raw_depth < 100, 1, 0)
  ) %>% 
  rename(temp = temperature_c, do = do_mlpl)

# scale predictors before filtering to ensure mean and SD are global
d <- gfranges::scale_predictors(d, 
  predictors = c(quo(depth), quo(sandy), quo(muddy), quo(temp), quo(do), quo(roms))
)

# # rename raw_depth for plots 
# d <- d %>% mutate(depth = raw_depth) %>%
#   filter(ssid %in% model_ssid) 

### trim for the climate variable of interest
if (clim_cov %in%  "temp"){ d <- d[!is.na(d$temp), ]}
if (clim_cov %in% "roms"){ d <- d[!is.na(d$roms), ]}
if (clim_cov %in% "do"){ d <- d[!is.na(d$do), ]}

data <- d 

# merge survey pairs such that even year surveys are modelled as though they occured in the previous odd year
data <- data %>% 
  filter(year > 2003) %>% 
  # trick to round to odd years
  # 0.8 is required to avoid 5's always rounding to even in R
  mutate(year_pair = (2 * round((year+0.8)/2))-1) %>% 
  filter(year < 2019)
```

Plots illustrating year pairs and location of samples where species was caught
```{r}
ggplot() + geom_point(data = filter(data, present == 0), 
    aes(X, Y, colour = sandy), # color absent points with proportion sandy
    shape= 1, alpha=0.5, size=2) +
  geom_point(data = filter(data, present == 1), aes(X, Y, size = density), 
    shape = 4) +
  scale_color_viridis_c(trans=fourth_root_power, option = "A", begin = 0.4) +
  facet_wrap(~year)

ggplot() + geom_point(data = filter(data, present == 0), 
    aes(X, Y, colour = sandy), 
    shape= 1, alpha=0.5, size=2) +
    geom_point(data = filter(data, present == 1), aes(X, Y, size = density), 
    shape = 4) +
  scale_color_viridis_c(trans=fourth_root_power, option = "A", begin = 0.4) +
  facet_wrap(~year_pair)
```

All years plotted at once
```{r}
ggplot() + geom_point(data = filter(data, present == 0), 
    aes(X, Y, colour = sandy), 
    shape= 1, alpha=0.65, size=2) +
  geom_point(data = filter(data, present == 1), aes(X, Y, size = density), 
    shape = 4) +
  scale_color_viridis_c(option = "A", trans=fourth_root_power, begin = 0.4) +
  geom_abline(intercept = 0, slope = 1)
```



```{r eval = FALSE}
# depth diff = difference between bath and sample depths
# depth range is difference between start and end sample depths
ggplot(data, aes(depth_sam, depth_bath, colour = depth_range)) + 
  geom_point(alpha=0.75) +
  scale_color_viridis_c(trans=fourth_root_power, direction = -1) +
  geom_abline(intercept = 0, slope = 1)

# # current data set includes only sampled depths with no bathymetry based depths
# ggplot(data, aes(raw_depth, depth_bath, colour = depth_range)) + 
#   geom_point(alpha=0.75) +
#   scale_color_viridis_c(trans=fourth_root_power, direction = -1) +
#   geom_abline(intercept = 0, slope = 1)

ggplot(data, aes(depth_sam, depth_range, colour = as.factor(ssid))) + 
  geom_point(alpha=0.75) +
  scale_color_viridis_d() 
```

Check ROMS vs. CTD temperature measurements
```{r eval= FALSE}
# differences between bath and sample depths doesn't seem to explain differences between sample values and roms
# these roms values are an average of April through September vs. single CTD measurements 
ggplot(data, aes(roms, temp, colour = depth_diff)) + 
  geom_point(alpha=0.75, size=0.5) +
  scale_color_viridis_c(trans=fourth_root_power, direction = -1) +
  geom_abline(intercept = 0, slope = 1) +
  xlab("ROMS mean (April - September)") +
  ylab("ctd temperature")

# differences between start and end depths also don't seem to explain differences between sample values and roms
ggplot(data, aes(roms, temp, colour = depth_range)) + 
  geom_point(alpha=0.75, size=0.5)  +
  scale_color_viridis_c(trans=fourth_root_power, direction = -1) +
  geom_abline(intercept = 0, slope = 1) +
  xlab("ROMS mean (April - September)") +
  ylab("ctd temperature")
```

Check for substrate correlations -- sandy somewhat correlated with depth
```{r}
ggplot(data, aes(raw_depth, sandy, colour = raw_depth)) + 
  geom_point(alpha=0.75, size=0.5) +
  scale_color_viridis_c(trans=fourth_root_power, direction = -1) 

ggplot(filter(data, raw_depth < 100), aes(raw_depth, sandy, colour = raw_depth)) + 
  geom_point(alpha=0.75, size=0.5) +
  scale_color_viridis_c(trans=fourth_root_power, direction = -1) 

ggplot(data, aes(raw_depth, muddy, colour = raw_depth)) + 
  geom_point(alpha=0.75, size=0.5) +
  scale_color_viridis_c(trans=fourth_root_power, direction = -1) 

# ggplot(data, aes(raw_depth, sandy-muddy, colour = raw_depth)) + 
#   geom_point(alpha=0.75, size=0.5) +
#   scale_color_viridis_c(trans=fourth_root_power, direction = -1) 
```


Make mesh
```{r}
data <- data %>% filter(ssid %in% model_ssid)

if (region == "Both odd year surveys") {
  spde <- sdmTMB::make_spde(data$X, data$Y, n_knots = 250)
}

if (region == "West Coast Vancouver Island") {
  spde <- sdmTMB::make_spde(data$X, data$Y, n_knots = 200)
}

if (region == "All synoptic surveys") {
  spde <- sdmTMB::make_mesh(data, c("X", "Y"), n_knots = knots)
}

if (region == "Non-HG surveys") {
  spde <- sdmTMB::make_mesh(data, c("X", "Y"), n_knots = knots)
}
plot(spde)
```


Run sdmTMB model
```{r }
if (params$update_model) {
  
    total_biomass <- sdmTMB::sdmTMB(
      data = data, mod.formula,
      time = "year_pair", spde = spde,
      family = tweedie(link = "log"),
      ar1_fields = params$AR1,
      reml = params$REML,
      include_spatial = params$fixed_spatial
    )

    saveRDS(total_biomass, file = paste0(
      "models/", spp, "/mod-tot-biomass-", spp, 
      covs, "-", ssid_string, "-ar1-", params$AR1, "-reml-", params$REML, params$knots, ".rds"
    ))
}
```

### Check residuals
```{r}
if(params$update_model_check) {

m <- readRDS(paste0(
  "models/", spp, "/mod-tot-biomass-", spp, 
  covs, "-", ssid_string, "-ar1-", params$AR1, 
  "-reml-", params$REML, params$knots, ".rds"
  ))

point_predictions <- predict(m)
point_predictions$residuals <- residuals(m)

saveRDS(point_predictions, file = paste0(
  "data/", spp, "/check-mod-predictions-", spp, 
  covs, "-", ssid_string, "-ar1-", params$AR1, "-reml-", 
  params$REML, params$knots, ".rds"
))
}
```

```{r}
pred <- readRDS(paste0(
  "data/", spp, "/check-mod-predictions-", spp, 
  covs, "-", ssid_string, "-ar1-", params$AR1, "-reml-", params$REML, params$knots, ".rds"
))

qqnorm(pred$residuals);abline(a = 0, b = 1)
```

```{r}
g <- ggplot(pred, 
    aes(density, residuals, colour = as.factor(ssid))) +
  geom_point() + scale_x_continuous(trans = "log10") +  
  facet_wrap(~year_pair)
g
```

```{r}
g1 <- ggplot(pred,
      aes(density, exp(est), colour = as.factor(ssid))) +
    geom_abline(slope=1, intercept = 0) +
    scale_x_continuous(trans = 'log10') +
    scale_y_continuous(trans = 'log10') +
    geom_point(alpha = 0.2) 
g1
```


```{r}
g2 <- ggplot(pred, 
      aes(exp(est), residuals, colour = density)) +
    geom_point(alpha = 0.2) + 
    scale_x_continuous(trans = 'log10') +
    facet_wrap(~year)
g2
```


```{r}
# ggplot(pred, aes(X, Y, colour = (residuals))) +
#   geom_point() +
#   scale_colour_gradient2() +
#   scale_x_continuous(trans = "log10") +
#   facet_wrap(~year)

ggplot(pred, aes(X, Y, colour = residuals)) +
  geom_point(size=0.5) +
  scale_colour_gradient2() +
  facet_wrap(~year_pair)
```


### Model summary
```{r }
if(!exists("m")){
m <- readRDS(paste0(
    "models/", spp, "/mod-tot-biomass-", spp, 
      covs, "-", ssid_string, "-ar1-", params$AR1, "-reml-", params$REML, params$knots, ".rds"
  ))
}
m
max(m$gradients)
```

### Effect plots
```{r}
threshold <- quantile(data$density, 0.999)
if(params$update_model_check){
  
nd_depth <- data.frame(
  depth_scaled = seq(min(data$depth_scaled), 
    max(data$depth_scaled), length.out = 30), 
  shallow = 1,
  sandy_scaled = 0,
  muddy_scaled = 0,
  temp_scaled = 0,
  roms_scaled = 0,
  year_pair = 2011 # a chosen year
)

p_depth <- predict(m, newdata = nd_depth, se_fit = TRUE, re_form = NA)
p_depth$depth <- exp((p_depth$depth_scaled*data$depth_sd[1])+ data$depth_mean[1])

max_CI <- max(exp(p_depth$est + 1.96 * p_depth$est_se))
max_Y <- if_else(threshold > max_CI, max_CI, threshold)  

(g_depth <- ggplot(p_depth, aes(depth, exp(est), 
  ymin = exp(est - 1.96 * est_se), 
  ymax = exp(est + 1.96 * est_se))) +
  coord_cartesian(ylim = c(0, max_Y), xlim = c(0, 150)) +
  geom_line() + geom_ribbon(alpha = 0.4))

ggsave(paste0("figs/depth-", spp, covs, ".png"), width = 5, height = 5)
}
try({g_depth}, silent = TRUE)
```


```{r}
if(clim_cov == "roms"){
nd_roms <- data.frame(
  depth_scaled = min(data$depth_scaled), # use min depth for estimated prob at most relevant depth
  shallow = 1,
  sandy_scaled = 0,
  muddy_scaled = 0,
  roms_scaled = seq(min(data$roms_scaled), 
    max(data$roms_scaled), length.out = 50),
  year_pair = 2011 # a chosen year
)
p_roms <- predict(m, newdata = nd_roms, se_fit = TRUE, re_form = NA)
p_roms$roms <- (p_roms$roms_scaled*data$roms_sd[1])+ data$roms_mean[1]

max_CI <- max(exp(p_roms$est + 1.96 * p_roms$est_se))
max_Y <- if_else(threshold > max_CI, max_CI, threshold)  

(g_roms <- ggplot(p_roms, aes(roms, exp(est), 
  ymin = exp(est - 1.96 * est_se), 
  ymax = exp(est + 1.96 * est_se))) +
  coord_cartesian(ylim = c(0, max(exp(p_roms$est))*20)) +
  geom_line() + geom_ribbon(alpha = 0.4))

ggsave(paste0("figs/roms-", spp, covs, ".png"), width = 5, height = 5)
}

try({g_roms}, silent = TRUE)
```


```{r}
if(clim_cov == "temp"){
nd_temp <- data.frame(
  depth_scaled = min(data$depth_scaled), 
  shallow = 1,
  sandy_scaled = 0,
  muddy_scaled = 0,
  temp_scaled = seq(min(data$temp_scaled), 
    max(data$temp_scaled), length.out = 50),
  year_pair = 2011 # a chosen year
)
p_temp <- predict(m, newdata = nd_temp, se_fit = TRUE, re_form = NA)
p_temp$temp <- (p_temp$temp_scaled*data$temp_sd[1])+ data$temp_mean[1]

max_CI <- max(exp(p_temp$est + 1.96 * p_temp$est_se))
max_Y <- if_else(threshold > max_CI, max_CI, threshold)  

(g_temp <- ggplot(p_temp, aes(temp, exp(est), 
  ymin = exp(est - 1.96 * est_se), 
  ymax = exp(est + 1.96 * est_se))) +
  coord_cartesian(ylim = c(0, max_Y)) +
  geom_line() + geom_ribbon(alpha = 0.4))

ggsave(paste0("figs/temp-", spp, covs, ".png"), width = 5, height = 5)
}
try({g_temp}, silent = TRUE)
```

```{r}
if(covs %in% c("-sand-depth-roms", "-sand-depth-temp", "-mud-sand-depth-temp")){
nd_sand <- data.frame(
  depth_scaled = min(data$depth_scaled), 
  shallow = 1,
  sandy_scaled = seq(min(data$sandy_scaled), 
    max(data$sandy_scaled), length.out = 50),
  muddy_scaled = min(data$muddy_scaled),
  roms_scaled = 0,
  temp_scaled = 0,
  year_pair = 2011 # a chosen year
)

p_sand <- predict(m, newdata = nd_sand, se_fit = TRUE, re_form = NA)
p_sand$sandy <- (p_sand$sandy_scaled*data$sandy_sd[1])+ data$sandy_mean[1]

(g_sand <- ggplot(p_sand, aes(sandy, exp(est),
  ymin = exp(est - 1.96 * est_se), 
  ymax = exp(est + 1.96 * est_se))) +
  coord_cartesian(ylim = c(0, max_Y)) +
  geom_line() + geom_ribbon(alpha = 0.4))

ggsave(paste0("figs/sand-", spp, covs, ".png"), width = 5, height = 5)
}
try({g_sand}, silent = TRUE)
```


```{r}
if(covs %in% c("-mud-depth-roms", "-mud-depth-temp","-mud-sand-depth-temp")){
nd_mud <- data.frame(
  depth_scaled = min(data$depth_scaled), 
  shallow = 1,
  muddy_scaled = seq(min(data$muddy_scaled), 
    max(data$muddy_scaled), length.out = 50),
  sandy_scaled = max(data$sandy_scaled),
  roms_scaled = 0,
  temp_scaled = 0,
  year_pair = 2011 # a chosen year
)

p_mud <- predict(m, newdata = nd_mud, se_fit = TRUE, re_form = NA)
p_mud$muddy <- (p_mud$muddy_scaled*data$muddy_sd[1])+ data$muddy_mean[1]

max_CI <- max(exp(p_mud$est + 1.96 * p_mud$est_se))
max_Y <- if_else(threshold > max_CI, max_CI, threshold)

(g_mud <- ggplot(p_mud, aes(muddy, exp(est),
  ymin = exp(est - 1.96 * est_se), 
  ymax = exp(est + 1.96 * est_se))) +
  coord_cartesian(ylim = c(0, max_Y)) +
  geom_line() + geom_ribbon(alpha = 0.4))

ggsave(paste0("figs/mud-", spp, covs, ".png"), width = 5, height = 5)
}
try({g_mud}, silent = TRUE)
```


### Map biomass predictions 

Save predictions for spatial grid
```{r}
rm(ad_predictions)
rm(im_predictions)
rm(predicted)

if(params$update_predictions) {
  newcov <- readRDS("data/new_covariates.rds") %>% 
    dplyr::select(X, Y, sandy, muddy, rocky, mixed)
  
  nd_all <- readRDS(
    here::here("analysis/VOCC/data/predicted-all-temp-with-roms.rds")
    # paste0("data/predicted-DO-2020-06-20-more2016-roms.rds")
    ) %>% dplyr::select(X, Y, year, ssid, depth, roms = roms_temp, temp)
  
  scaledata <- data %>% 
    dplyr::select(depth_mean, depth_sd, 
      sandy_mean, sandy_sd,  muddy_mean, muddy_sd, 
      roms_mean, roms_sd, temp_mean, temp_sd)
  
  nd_all <- left_join(nd_all, newcov) 
  
  nd_all$depth_mean <- scaledata$depth_mean[1]
  nd_all$depth_sd <- scaledata$depth_sd[1]
  nd_all$sandy_mean <- scaledata$sandy_mean[1]
  nd_all$sandy_sd <- scaledata$sandy_sd[1]
  nd_all$muddy_mean <- scaledata$muddy_mean[1]
  nd_all$muddy_sd <- scaledata$muddy_sd[1]
  nd_all$roms_mean <- scaledata$roms_mean[1]
  nd_all$roms_sd <- scaledata$roms_sd[1]
  nd_all$temp_mean <- scaledata$temp_mean[1]
  nd_all$temp_sd <- scaledata$temp_sd[1]
  
  nd_all <- nd_all %>% mutate(
    depth_scaled = (log(depth) - depth_mean)/depth_sd,
    sandy_scaled = (sandy - sandy_mean)/sandy_sd,
    muddy_scaled = (muddy - muddy_mean)/muddy_sd,
    roms_scaled = (roms - roms_mean)/roms_sd,
    temp_scaled = (temp - temp_mean)/temp_sd
  ) 
  nd_all <- nd_all %>% filter(year > 2003) %>% 
  # merge survey pairs such that even year surveys are pooled w the previous odd year
    # 0.8 is required to avoid 5s rounding to even in R
    mutate(year_pair = (2 * round((year+0.8)/2))-1,
      shallow = if_else(depth < 100, 1, 0)) %>% 
    filter(year < 2019)

  m <- readRDS(paste0("models/", spp, "/mod-tot-biomass-", spp, 
    covs, "-", ssid_string, "-ar1-", params$AR1, "-reml-", params$REML, params$knots, ".rds"
  ))

  nd <- nd_all %>%
    filter(ssid %in% model_ssid) %>%
    filter(year %in% unique(m$data$year))
  nd <- na.omit(nd)
  # nd$year <- as.integer(nd$year)

  predicted <- predict(m, newdata = nd, se_fit = F, return_tmb_object = T)
  
  saveRDS(predicted, file = paste0(
    "data/", spp, "/predictions-", spp, 
    covs, "-", ssid_string, "-tot-biomass-ar1-", params$AR1, "-reml-", params$REML, params$knots, ".rds"
  ))
}
```

Transform estimates to biomass density in kg/ha
```{r}
rm(predictions)
rm(predicted)


  predicted <- readRDS(paste0("data/", spp, "/predictions-", spp, 
      covs, "-", ssid_string, "-tot-biomass-ar1-", 
      params$AR1, "-reml-", params$REML, params$knots, ".rds"
    ))


  predictions <- predicted$data
  predictions$total_bio <- exp(predictions$est) 
  max_raster <- quantile(predictions$total_bio, 0.999)
  max_bio <- signif(quantile(predictions$total_bio, 1), digits = 2)

  predictions$prop_max <- predictions$total_bio/max_raster
  
  saveRDS(predictions, file = paste0(
    "data/", spp,
    "/just-predictions-", spp, covs, "-total-biomass-ar1-", 
    params$AR1, "-reml-", params$REML, params$knots, ".rds"
  ))
```




```{r, error=TRUE}
legend_coords <- c(0.12, 0.2) #"none"

p_mean <- predictions  %>% group_by(X, Y) %>%
  mutate(mean_est = mean(exp(est))) %>% 
  filter(year_pair == 2011) %>% 
  mutate(year = "all years") %>%
  plot_facet_map("mean_est",
    raster_limits = c(0, max_raster),
    transform_col = fourth_root_power,
    legend_position = legend_coords
  ) + labs(fill = "kg/ha") +
  ggtitle(paste0("Estimated biomass density of ", species, 
    " \n(max = ", max_bio, " kg/ha)"))
print(p_mean)
ggsave(paste0("figs/map-", spp, covs, "-mean-biomass.png"), width = 5, height = 5)
```

Spatial random field - captures variance not explained by depth and temperature
```{r, error=TRUE}
legend_coords <- c(0.12, 0.2) #"none"

p_omega <- predictions  %>% filter(year_pair == 2011) %>%
  mutate(x = X, y = Y, year = year_pair) %>%
  filter(year_pair == 2011) %>% 
  mutate(year = "all years") %>%
  plot_facet_map("omega_s",
    # raster_limits = c(0, 1),
    # transform_col = fourth_root_power,
    legend_position =  legend_coords
  ) + ggtitle(paste0("Spatial random field"))

print(p_omega)

ggsave(paste0("figs/map-", spp, covs, "-spatial-rf.png"), 
  width = 5, height = 5)
```

Spatiotemporal random fields
```{r, error=TRUE}
legend_coords <- c(0.9, 0.12) #"none"

p_st <- predictions  %>% 
  mutate(x = X, y = Y) %>%
  plot_facet_map("epsilon_st",
    legend_position = legend_coords,
    transform_col = fourth_root_power
  ) +
    ggtitle(paste0("Spatiotemporal random fields"))

print(p_st)
ggsave(paste0("figs/map-", spp, covs, "-spatiotemporal-rf.png"), 
  width = 5, height = 5)
```

