---
output: html_document
editor_options: 
  chunk_output_type: inline
---
# Fit spatial temporal models to bottom temperature

```{r setup}
library(tidyverse)
library(sdmTMB)
library(future)
library(dplyr)

plan(multiprocess)
```

Load data
```{r}
all_sensor <- readRDS(here::here("analysis/tmb-sensor-explore/data/dat-sensor-trawl-meanSST-all.rds"))
# all_sensor <- readRDS(here::here("analysis/tmb-sensor-explore/data/dat-sensor-trawl-processed.rds")) # no SST
# glimpse(all_sensor)
# 
# replace obviously faulty depth data with NA
#all_sensor$depth_m[all_sensor$depth_m < 10] <- NA # 5,139 

all_depth <- all_sensor %>%
  #filter(depth_max>10) %>% # maybe we should filter incase missing depth values also indicate a sensor fail?
  # filter missing location data and trial year
  dplyr::filter(!is.na(latitude), !is.na(longitude)) %>%

  # convert lat and lon to UTMs
  dplyr::mutate(X = longitude, Y = latitude) %>%
  gfplot:::ll2utm(., utm_zone = 9) %>% 

  # interpolate missing depth values
  dplyr::rename(depth = depth_m) %>%
  gfplot:::interp_survey_bathymetry()

unique(all_depth$data$year)


d_trawl <- all_depth$data %>% 
  # remove obvious sensor fails, d_trawl %>% filter(depth_max<10), fishing event ids = 481861, 2179089
  filter(depth_max>10) %>% 
  # filter(ssid != 1) %>%
  # filter(ssid != 3) %>%
  # filter(ssid != 4) %>%
  # filter(ssid != 16) %>%
  gfplot:::scale_survey_predictors()

hist(d_trawl$temperature_c)

d_trawl <- d_trawl[!is.na(d_trawl$depth), ]
d_trawl <- d_trawl[!is.na(d_trawl$temperature_c), ]
d_trawl <- d_trawl[!is.na(d_trawl$SST), ]
d_trawl <- d_trawl[!is.na(d_trawl$meanSST), ]
d_trawl <- mutate(d_trawl,
  DOY = lubridate::yday(date),
  DOY_scaled = arm::rescale(lubridate::yday(date)),
  DOY_scaled2 = arm::rescale(lubridate::yday(date))^2,
  #depth_scaled = arm::rescale(log(depth_m)),
  SST_scaled = arm::rescale(meanSST),
  #depth_scaled2 = depth_scaled^2,
  depth_scaled3 = depth_scaled^3,
  shallow = ifelse(depth>35,0,1),
    deep = ifelse(depth<35,0,1)
)
# d_trawl[is.na(d_trawl$shallow), ]
# d_trawl[is.na(d_trawl$SST_scaled), ]

glimpse(d_trawl)

d_trawl <- d_trawl %>% dplyr::filter(year>2003)
```

Explore SST 
```{r}
ggplot(d_trawl, aes_string("X", "Y", colour = "SST")) +
    geom_point() +
    facet_wrap(~year) +
    coord_fixed() +
    scale_color_viridis_c()
```
```{r}
ggplot(d_trawl, aes(DOY, SST, colour = -depth)) + geom_point() + facet_wrap(~year) 
```

```{r}
ggplot(dplyr::filter(d_trawl, depth <35), aes(SST,temperature_c, colour = -depth)) + geom_point()
ggplot(dplyr::filter(d_trawl, depth <35), aes(SST,temperature_c, colour = DOY)) + geom_point()

```

Explore mean SST 
```{r}
ggplot(d_trawl, aes_string("X", "Y", colour = "meanSST")) +
    geom_point() +
    facet_wrap(~year) +
    coord_fixed() +
    scale_color_viridis_c()
```

```{r}
ggplot(dplyr::filter(d_trawl1, shallow==1), aes(SST_scaled,temperature_c, colour = -depth)) + geom_point()
```


EXLORE TEMPERATURE at DEPTH

```{r}
ggplot(d_trawl, aes_string("X", "Y", colour = "temperature_c")) +
    geom_point() +
    facet_wrap(~year) +
    coord_fixed() +
    scale_color_viridis_c()
```


```{r}
ggplot(d_trawl, aes(log(depth),temperature_c, colour = depth_max)) + geom_point() + facet_wrap(~ssid)
```

```{r}
ggplot(d_trawl, aes(DOY, temperature_c, colour = -depth, alpha=0.5)) + geom_point() + facet_wrap(~year) 
```

```{r}
d_trawl1 <- d_trawl %>% filter(ssid == 3)
spde <- make_spde(d_trawl1$X, d_trawl1$Y, n_knots = 150)
plot_spde(spde)
sum(d_trawl1$shallow)
```


```{r}
d_trawl1$year_scaled <- arm::rescale(d_trawl1$year)
d_trawl1$x_scaled <- arm::rescale(d_trawl1$X)
d_trawl1$y_scaled <- arm::rescale(d_trawl1$Y)

m_temp_SST <- sdmTMB(d_trawl1,
  temperature_c ~ year_scaled + poly(SST_scaled,3)*depth_scaled , #+ SST_scaled*x_scaled + SST_scaled*y_scaled
  #time_varying = ~ 0 + depth_scaled2,
  ar1_fields = FALSE, include_spatial = FALSE,
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = FALSE
)

p_SST <- predict(m_temp_SST)

p_SST$residuals <- residuals(m_temp_SST)

ggplot(p_SST, aes(depth_scaled, residuals)) +
  geom_point(alpha=0.4) +
  ylim(-8,8) +
  geom_smooth()



```



```{r}
library(gbm)

m <- gbm( temperature_c ~ depth_scaled + X + Y, data = d_trawl1, n.trees = 2000, interaction.depth = 3, shrinkage = 0.02)

m2 <- gbm( temperature_c ~ SST_scaled + depth_scaled + X + Y, data = d_trawl1, n.trees = 2000, interaction.depth = 3, shrinkage = 0.02)

plot(m,i.var=2)
plot(m,i.var=3)
plot(m,i.var=4)
plot(m,i.var=5)


plot(m2,i.var=1)
plot(m2,i.var=2)
plot(m,i.var=3)
plot(m,i.var=4)

plot(m2,i.var=1:2)
plot(m2,i.var=c(1,3))
plot(m2,i.var=c(1,4))
d_trawl$r <- predict(m, n.trees = 2000) - d_trawl1$temperature_c

ggplot(d_trawl, aes(depth_scaled, r)) +
  geom_point(alpha=0.4) +
  ylim(-8,8) +
  geom_smooth()
```

```{r}

p_SST <- predict(m_temp_SST)
p <- predict(m_temp)
#predictions3b <- predict(m_temp3_nosst)

p_SST$residuals <- residuals(m_temp_SST)
p$residuals <- residuals(m_temp)

# nd <- data.frame(sst_resid = predictions3$data$residuals, nosst_resid = predictions3b$data$residuals, shallow = d_trawl$shallow, depth = d_trawl$depth)
# 
# ggplot(filter(nd, shallow == 1), aes(nosst_resid,sst_resid, colour = as.factor(shallow))) + 
#   geom_point() + geom_abline(intercept = 0, slope = 1)
```
Residual plots:
```{r}
ggplot(p_SST, aes(est, residuals)) +
  geom_point() +
  geom_smooth() +
  ylim(-8,8) +
  xlim(2,15) +
  facet_wrap(~year)
ggplot(p, aes(est, residuals)) +
  geom_point() +
  geom_smooth() +
  ylim(-8,8) +
   xlim(2,15) +
  facet_wrap(~year)
```

```{r}
ggplot(p_SST, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth() +
  ylim(-7,8) +
  facet_wrap(~year)
ggplot(p, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth() +
  ylim(-7,8) +
  facet_wrap(~year)
```

```{r}
p_SST$depth_mean <- exp(p_SST$depth_scaled*0.66+5)
glimpse(d_trawl)
ggplot(d_trawl, aes(depth_scaled, r)) +
  geom_point(alpha=0.4) +
  ylim(-8,8) +
  geom_smooth()
```


```{r}
p1 <- ggplot(p_SST, aes(depth_scaled, residuals)) +
  geom_point() +
  ylim(-8,8) +
  geom_smooth()
p2 <- ggplot(p, aes(depth_scaled, residuals)) +
  geom_point() +
  ylim(-8,8) +
  geom_smooth()
gridExtra::grid.arrange(p1, p2, nrow = 2)
```

### Functions for model exploration:
```{r}
# aic <- function(m) {
#   k <- length(m$model$par)
#   nll <- m$model$objective
#   2 * k - 2 * (-nll)
# }

generate_cv_args <- function(
                             formula = formula,
                             time_varying = time_varying,
                             ar1_fields = c(FALSE), # simiple, fast defaults
                             include_spatial = c(FALSE), # simiple, fast defaults
                             n_knots = c(100), # simiple, fast defaults
                             seed = c(999)) {
  arguments <- expand.grid(
    formula = formula,
    time_varying = time_varying,
    include_spatial = include_spatial,
    ar1_fields = ar1_fields,
    n_knots = n_knots,
    seed = seed
  )
  as.data.frame(arguments)
}

sdmTMB_cv_batch <- function(cv_args, data, ...) {
  cv_batch <- purrr::pmap(cv_args, sdmTMB_cv, data = d_trawl, ...)
  cv_out <- cv_args
  cv_out$cv_loglik <- c()
  cv_out$all_converged <- c()
  cv_out$max_grad <- c()
  for (i in seq_len(nrow(cv_args))) {
    cv_out$cv_loglik[[i]] <- round(cv_batch[[i]]$sum_loglik, 1)
    cv_out$all_converged[[i]] <- all(cv_batch[[i]]$converged)
    cv_out$max_grad[[i]] <- max(cv_batch[[i]]$max_grad)
    if (is.null(cv_out$time_varying[[i]])) {
      cv_out$time_varying[[i]] <- as.character(NA)
    }
  }
  cv_out$formula <- as.character(cv_out$formula)
  cv_out$time_varying <- as.character(cv_out$time_varying)

  cv_out <- cv_out %>%
    group_by(seed) %>%
    mutate(., max_ll_per_seed = max(cv_loglik)) %>%
    mutate(., delta_ll = cv_loglik - max_ll_per_seed) %>%
    ungroup()
  row.names(cv_out) <- NULL
  list(summary = as.data.frame(cv_out), cv_model_set = cv_batch)
}

# # this code keeps breaking... working, fails, worked again, then failed again...
# plot_cv_meshes <- function(sdmTMB_cv_output) {
#   cv_output <- sdmTMB_cv_output
#   k <- max(cv_output$data$cv_fold) # should probably rename cv_fold to fold_id
#   if (k == 2 | k == 5 | k == 10) {
#     op <- graphics::par(
#       mfrow = c((sqrt(k)), ceiling(sqrt(k))),
#       mar = c(1, 1, 1, 1)
#       )
#   } else {
#     op <- graphics::par(
#       mfrow = c(ceiling(sqrt(k)), ceiling(sqrt(k))),
#       mar = c(1, 1, 1, 1)
#     )
#   }
#   for (i in seq_len(k)){
#     plot_spde(cv_output$models[[i]]$spde)
# #FIXME: Error in xy.coords(x, y, xlabel, ylabel, log) :
# #  'x' is a list, but does not have components 'x' and 'y'
#   }
#   graphics::par(op)
# }
```


Short example: 
```{r, eval=FALSE}
cv_args <- generate_cv_args(
  formula = list(
    temperature_c ~ 0 + as.factor(year) + SST_scaled + depth_scaled + depth_scaled2 + depth_scaled3
  ),
  time_varying = list(NULL),
  ar1_fields = c(FALSE),
  include_spatial = c(FALSE),
  n_knots = c(135, 140, 145, 150),
  seed = c(1)
)

cv <- sdmTMB_cv_batch(cv_args, d_trawl, k_folds = 4, time = "year", x = "X", y = "Y")
glimpse(cv$summary)
write.csv(cv$summary, file = "cv-output/cv-test.csv")
cv_test <- read_csv(file = "cv-output/cv-test.csv")
View(cv$summary)
# plot_cv_meshes(cv$cv_model_set[[1]])
# plot_cv_meshes(cv$cv_model_set[[2]])
```

# 10-fold cross-validation 

## Just compare fixed slope models with simplest random effect structure
```{r}
cv_args <- generate_cv_args(
  formula = list(
    temperature_c ~ 0 + SST_scaled*shallow + depth_scaled,
    temperature_c ~ 0 + SST_scaled*shallow + depth_scaled + depth_scaled2,
    temperature_c ~ 0 + SST_scaled*shallow + depth_scaled + depth_scaled2 + depth_scaled3,
    temperature_c ~ 1 + SST_scaled + depth_scaled,
    temperature_c ~ 1 + SST_scaled + depth_scaled + depth_scaled2,
    temperature_c ~ 1 + SST_scaled + depth_scaled + depth_scaled2 + depth_scaled3,
    temperature_c ~ 0 + as.factor(year) + depth_scaled,
    temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2,
    temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2 + depth_scaled3,
    temperature_c ~ 0 + as.factor(year) + SST_scaled + depth_scaled,
    temperature_c ~ 0 + as.factor(year) + SST_scaled + depth_scaled + depth_scaled2,
    temperature_c ~ 0 + as.factor(year) + SST_scaled + depth_scaled + depth_scaled2 + depth_scaled3,
    temperature_c ~ 0 + as.factor(year) + SST_scaled * depth_scaled,
    temperature_c ~ 0 + as.factor(year) + SST_scaled * depth_scaled + SST_scaled * depth_scaled2,
    temperature_c ~ 0 + as.factor(year) + SST_scaled * depth_scaled + SST_scaled * depth_scaled2 + SST_scaled * depth_scaled3
  ),
  time_varying = list(NULL),
  ar1_fields = c(FALSE),
  include_spatial = c(FALSE),
  n_knots = c(100),
  seed = c(1111, 2222, 3333, 4444)
)

non_time_varying <- sdmTMB_cv_batch(cv_args, d_trawl, time = "year", x = "X", y = "Y")
View(non_time_varying$summary)
write.csv(non_time_varying$summary, file = "cv-output/cv-non-time-varying.csv")
saveRDS(non_time_varying, file = "cv-output/cv-non-time-varying.rds")
glimpse(non_time_varying$summary)
```

## Compare time-varying slope models still with simplest random effect structure
All of top models for any seed contained year and none showed a linear effect of depth
All are better than fixed slope models
```{r}
cv_args <- generate_cv_args(
  formula = list(
    #temperature_c ~ 0 + SST_scaled*shallow,
    temperature_c ~ 0 + as.factor(year) + SST_scaled*shallow,
    #temperature_c ~ 1 + SST_scaled,
    temperature_c ~ 0 + as.factor(year) + SST_scaled,
    temperature_c ~ 0 + as.factor(year)
  ),
  time_varying = list(
    ~ 0 + depth_scaled + depth_scaled2,
    ~ 0 + depth_scaled + depth_scaled2 + depth_scaled3
  ),
  ar1_fields = c(FALSE),
  include_spatial = c(FALSE),
  n_knots = c(100), # keep same n_knots
  seed = c(1111, 2222, 3333, 4444) # keep same seeds
)

time_varying <- sdmTMB_cv_batch(cv_args, d_trawl, time = "year", x = "X", y = "Y")

View(time_varying$summary)
write.csv(time_varying$summary, file = "cv-output/cv-time-varying.csv")
saveRDS(time_varying, file = "cv-output/cv-time-varying.rds")
glimpse(time_varying$summary)
```


## Now vary random effect configuation for top model(s) 
a separate spatial field is in all models with highest likelihoods for each seed
AR1 doesn't make much difference (differences between years appear independent)
```{r}
cv_args <- generate_cv_args(
  formula = list(
    temperature_c ~ 0 + as.factor(year) + SST_scaled*shallow,
    temperature_c ~ 0 + as.factor(year) + SST_scaled,
    temperature_c ~ 0 + as.factor(year)
  ),
  time_varying = list(
    ~ 0 + depth_scaled + depth_scaled2
  ),
  ar1_fields = c(FALSE, TRUE),
  include_spatial = c(FALSE, TRUE),
  n_knots = c(100),
  seed = c(1111, 2222, 3333, 4444)
)

vary_rf <- sdmTMB_cv_batch(cv_args, d_trawl, time = "year", x = "X", y = "Y")

View(vary_rf$summary)
write.csv(vary_rf$summary, file = "cv-output/cv-varying-rf.csv")
saveRDS(vary_rf, file = "cv-output/cv-varying-rf.rds")
glimpse(vary_rf$summary)
```

## Change knot number

```{r}
cv_args <- generate_cv_args(
    formula = list(
    # temperature_c ~ 0 + as.factor(year) + SST_scaled,
    temperature_c ~ 0 + as.factor(year)
  ),
  time_varying = list(
    ~ 0 + depth_scaled + depth_scaled2
  ),
  ar1_fields = c(FALSE,TRUE),
  include_spatial = c(TRUE),
  n_knots = c(140,180,220,250),
  #seed = c(1111, 2222, 3333, 4444) 
  seed = c(5555, 6666, 7777, 8888, 9999)
)

more_knots <- sdmTMB_cv_batch(cv_args, d_trawl, time = "year", x = "X", y = "Y")

View(more_knots$summary)
write.csv(more_knots$summary, file = "cv-output/cv-more-knots2.csv")
saveRDS(more_knots, file = "cv-output/cv-more-knots2.rds")
glimpse(more_knots$summary)
```

## Change seeds 
Also increased knot number too 
Models without SST_scaled are usually better

```{r}
cv_args <- generate_cv_args(
    formula = list(
    temperature_c ~ 0 + as.factor(year) + SST_scaled*shallow,
    temperature_c ~ 0 + as.factor(year) + SST_scaled,
    temperature_c ~ 0 + as.factor(year)
  ),
  time_varying = list(
    ~ 0 + depth_scaled + depth_scaled2
  ),
  ar1_fields = c(FALSE, TRUE),
  include_spatial = c(TRUE, FALSE),
  n_knots = c(130),
  seed = c(5555, 6666, 7777, 8888, 9999)
)

more_seeds <- sdmTMB_cv_batch(cv_args, d_trawl, time = "year", x = "X", y = "Y")

View(more_seeds$summary)
write.csv(more_seeds$summary, file = "cv-output/cv-more-seeds.csv")
saveRDS(more_seeds, file = "cv-output/cv-more-seeds.rds")
glimpse(more_seeds$summary)
```


Load saved batches:
```{r, eval=FALSE}
# non_time_varying <- readRDS(file = "cv-output/cv-non-time-varying.rds")
# time_varying <- readRDS(file = "cv-output/cv-time-varying.rds")
# vary_rf <- readRDS(file = "cv-output/cv-varying-rf.rds")
# knot_refining <- readRDS(file = "cv-output/cv-refine-knots.rds")

non_time_varying <- read.csv(file = "cv-output/cv-non-time-varying.csv")
time_varying <- read.csv(file = "cv-output/cv-time-varying.csv")
vary_rf <- read.csv(file = "cv-output/cv-varying-rf.csv")
non_time_varying1 <- read.csv(file = "cv-output/cv-non-time-varying1.csv")
time_varying1 <- read.csv(file = "cv-output/cv-time-varying1.csv")
vary_rf1 <- read.csv(file = "cv-output/cv-varying-rf1.csv")
refine_knots1 <- read.csv(file = "cv-output/cv-refine-knots1.csv")
more_seeds <- read.csv(file = "cv-output/cv-more-seeds.csv")
more_seeds1 <- read.csv(file = "cv-output/cv-more-seeds1.csv")


all_cv_loglik <- rbind(
  non_time_varying,
  time_varying,
  vary_rf,
  non_time_varying1,
  time_varying1,
  vary_rf1,
  refine_knots1,
  more_seeds,
  more_seeds1,
  deparse.level = 1, make.row.names = TRUE
)

by_seed <- all_cv_loglik %>%
  group_by(seed) %>%
  mutate(., max_ll_per_seed = max(cv_loglik)) %>%
  mutate(., delta_ll = cv_loglik - max_ll_per_seed)

View(by_seed)
all_cv_loglik <- by_seed %>% ungroup()

write.csv(all_cv_loglik, file = "all_cv_loglik.csv")
```

Current top model
```{r}
plan(multiprocess)
temp_rw <- sdmTMB_cv(
  data = d_trawl, n_knots = 130, x = "X", y = "Y", k_folds = 10,
  formula = temperature_c ~ 0 + as.factor(year) + SST_scaled,
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  time = "year", family = gaussian(link = "identity"),
  ar1_fields = FALSE, include_spatial = TRUE, seed = 999
)
sum(temp_rw$sum_loglik)
```


```{r}
spde <- make_spde(d_trawl$X, d_trawl$Y, n_knots = 220)
plot_spde(spde)
```


```{r}
m_temp_rw <- sdmTMB(d_trawl,
  temperature_c ~ 0 + as.factor(year),
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = FALSE, include_spatial = TRUE,
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE
)

predictions_rw <- predict(m_temp_rw)
predictions_rw$data$residuals <- residuals(m_temp_rw)
cor(predictions_rw$data$est, predictions_rw$data$temperature_c)^2 #
# aic(m_temp3_rw)
```

Residual plots:
```{r}
ggplot(predictions_rw$data, aes(est, residuals)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)
```

```{r}
ggplot(predictions_rw$data, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)
```

```{r}
ggplot(predictions_rw$data, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth()
```

Does a fixed interaction with SST_scaled do any better?

```{r}
m_temp3 <- sdmTMB(d_trawl,
  temperature_c ~ 0 + as.factor(year) + SST_scaled*depth_scaled + SST_scaled*depth_scaled2 + SST_scaled*depth_scaled3,
  ar1_fields = FALSE, include_spatial = TRUE,
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE
)

predictions3 <- predict(m_temp3)
predictions3$data$residuals <- residuals(m_temp3)
cor(predictions3$data$est, predictions3$data$temperature_c)^2 #
```

```{r}
ggplot(predictions3$data, aes(est, residuals)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)
```

```{r}
ggplot(predictions3$data, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)
```

```{r}
ggplot(predictions3$data, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth()
```


# A functions for plotting our predictions:

```{r}
plot_map <- function(dat, column = "est") {
  ggplot(dat, aes_string("X", "Y", colour = column)) +
    geom_point() +
    facet_wrap(~year) +
    coord_fixed()
}

plot_map_raster <- function(dat, column = "est") {
  ggplot(dat, aes_string("X", "Y", fill = column)) +
    geom_raster() +
    facet_wrap(~year) +
    coord_fixed()
}
```


## Plotting predictions
#FIXME: DON'T HAVE SST TEMP FOR PREDICITON GRID YET...

```{r}
qcs_grid$depth_scaled3 <- (qcs_grid$depth_scaled)^3
predictions_nd <- predict(m_temp3_rw, newdata = qcs_grid)
# saveRDS(predictions3_rw_nd$data, file = "qcs-temp.rds")
```

```{r}
plot_map_raster(predictions_nd$data, "est") +
  scale_fill_viridis_c(trans = "sqrt", option = "C") +
  ggtitle("Prediction (fixed effects + all random effects)")
```

```{r}
plot_map_raster(predictions_nd$data, "est_fe") +
  ggtitle("Prediction (fixed effects only)") +
  scale_fill_viridis_c(trans = "sqrt")
```

```{r, eval=FALSE}
plot_map_raster(predictions_nd$data, "est_re_s") +
  ggtitle("Spatial random effects only") +
  scale_fill_gradient2(low = "navy", mid = "white", high = "darkred")
```

```{r}
plot_map_raster(predictions_nd$data, "est_re_st") +
  ggtitle("Spatiotemporal random effects only") +
  scale_fill_gradient2(low = "navy", mid = "white", high = "darkred")
```


```{r}
ggplot(predictions3_rw$data, aes(temperature_c, est)) +
  geom_point() +
  facet_wrap(~year) +
  coord_fixed() +
  xlim(3, 15) +
  ylim(3, 15) +
  geom_abline()
```


```{r}
temp_cog <- get_cog(predictions_nd)

temp_cog %>%
  reshape2::dcast(year ~ coord, value.var = "est") %>%
  ggplot(aes(X, Y, colour = year)) + geom_path(arrow = arrow()) +
  scale_color_viridis_c()
```

```{r}
temp_cog %>%
  ggplot(aes(year, est, ymin = lwr, ymax = upr)) +
  geom_line() +
  geom_ribbon(alpha = 0.2) +
  facet_wrap(~coord, scales = "free_y")
```
